---
title: "Hotspot Richness"
output: html_notebook
---



```{r}
library(bigrquery)
library(randomForest)
library(ggplot2)
library(reshape2)
library(rpart)
library(tidyverse)
```


```{r}
# Store the project id
projectid = "1040471158864"

# Set your query
sql <- "SELECT * FROM `endless-matter-297214.model.model_hotspot_richness_data`"

# Run the query and store the data in a dataframe
bq_dat <- bq_project_query(x = projectid, query = sql)

bq_table_fields(bq_dat)
```

```{r}
dataset <- bq_table_download(bq_dat, max_results = Inf, page_size = 500) 

```
```{r}
nrow(dataset)
```

```{r}
length(unique(dataset$city_name))
```

```{r}
dataset[dataset$city_name == '',]
```

```{r}
write_csv(dataset, "hotspot_data.csv")

dataset <- read_csv("hotspot_data.csv")

head(dataset)
```
```{r}
ggplot(dataset, aes(x = number_of_checklists, y = locality_project_richness)) +
  geom_point() +
  geom_smooth(method = "gam", formula = y ~ s(x))
```

```{r}
dataset$abs_latitude = abs(dataset$latitude)
data <- dataset[,c(
    "city_name",
    "locality_project_richness",
    "pop_2015",
    "number_of_checklists",
    "elevation",
    "latitude",
    "abs_latitude",
    "city_pc_bare",
    "city_pc_closed_forest_deciduous_broadleaf",
    "city_pc_closed_forest_deciduous_needle",
    "city_pc_closed_forest_evergreen_broadleaf",
    "city_pc_closed_forest_evergreen_needle",
    "city_pc_closed_forest_forest_mixed",
    "city_pc_closed_forest_forest_other",
    "city_pc_closed_forest_forest_total",
    "city_pc_cultivated",
    "city_pc_herbaceous_vegetation",
    "city_pc_herbaceous_wetland",
    "city_pc_moss_and_lichen",
    "city_pc_ocean",
    "city_pc_open_forest_deciduous_broadleaf",
    "city_pc_open_forest_deciduous_needle",
    "city_pc_open_forest_evergreen_broadleaf",
    "city_pc_open_forest_evergreen_needle",
    "city_pc_open_forest_forest_mixed",
    "city_pc_open_forest_forest_other",
    "city_pc_open_forest_forest_total",
    "city_pc_permanent_water",
    "city_pc_shrubs",
    "city_pc_snow",
    "city_pc_unknown",
    "city_pc_urban",
    "region_pc_bare",
    "region_pc_closed_forest_deciduous_broadleaf",
    "region_pc_closed_forest_deciduous_needle",
    "region_pc_closed_forest_evergreen_broadleaf",
    "region_pc_closed_forest_evergreen_needle",
    "region_pc_closed_forest_forest_mixed",
    "region_pc_closed_forest_forest_other",
    "region_pc_closed_forest_forest_total",
    "region_pc_cultivated",
    "region_pc_herbaceous_vegetation",
    "region_pc_herbaceous_wetland",
    "region_pc_moss_and_lichen",
    "region_pc_ocean",
    "region_pc_open_forest_deciduous_broadleaf",
    "region_pc_open_forest_deciduous_needle",
    "region_pc_open_forest_evergreen_broadleaf",
    "region_pc_open_forest_evergreen_needle",
    "region_pc_open_forest_forest_mixed",
    "region_pc_open_forest_forest_other",
    "region_pc_open_forest_forest_total",
    "region_pc_permanent_water",
    "region_pc_shrubs",
    "region_pc_snow",
    "region_pc_unknown",
    "region_pc_urban",
    "b500_avg_pop_density",
    "b500_pc_bare",
    "b500_pc_closed_forest_deciduous_broadleaf",
    "b500_pc_closed_forest_deciduous_needle",
    "b500_pc_closed_forest_evergreen_broadleaf",
    "b500_pc_closed_forest_evergreen_needle",
    "b500_pc_closed_forest_forest_mixed",
    "b500_pc_closed_forest_forest_other",
    "b500_pc_closed_forest_forest_total",
    "b500_pc_cultivated",
    "b500_pc_herbaceous_vegetation",
    "b500_pc_herbaceous_wetland",
    "b500_pc_moss_and_lichen",
    "b500_pc_ocean",
    "b500_pc_open_forest_deciduous_broadleaf",
    "b500_pc_open_forest_deciduous_needle",
    "b500_pc_open_forest_evergreen_broadleaf",
    "b500_pc_open_forest_evergreen_needle",
    "b500_pc_open_forest_forest_mixed",
    "b500_pc_open_forest_forest_other",
    "b500_pc_open_forest_forest_total",
    "b500_pc_permanent_water",
    "b500_pc_shrubs",
    "b500_pc_snow",
    "b500_pc_unknown",
    "b500_pc_urban",
    "b1km_avg_pop_density",
    "b1km_pc_bare",
    "b1km_pc_closed_forest_deciduous_broadleaf",
    "b1km_pc_closed_forest_deciduous_needle",
    "b1km_pc_closed_forest_evergreen_broadleaf",
    "b1km_pc_closed_forest_evergreen_needle",
    "b1km_pc_closed_forest_forest_mixed",
    "b1km_pc_closed_forest_forest_other",
    "b1km_pc_closed_forest_forest_total",
    "b1km_pc_cultivated",
    "b1km_pc_herbaceous_vegetation",
    "b1km_pc_herbaceous_wetland",
    "b1km_pc_moss_and_lichen",
    "b1km_pc_ocean",
    "b1km_pc_open_forest_deciduous_broadleaf",
    "b1km_pc_open_forest_deciduous_needle",
    "b1km_pc_open_forest_evergreen_broadleaf",
    "b1km_pc_open_forest_evergreen_needle",
    "b1km_pc_open_forest_forest_mixed",
    "b1km_pc_open_forest_forest_other",
    "b1km_pc_open_forest_forest_total",
    "b1km_pc_permanent_water",
    "b1km_pc_shrubs",
    "b1km_pc_snow",
    "b1km_pc_unknown",
    "b1km_pc_urban",
    "b2km_avg_pop_density",
    "b2km_pc_bare",
    "b2km_pc_closed_forest_deciduous_broadleaf",
    "b2km_pc_closed_forest_deciduous_needle",
    "b2km_pc_closed_forest_evergreen_broadleaf",
    "b2km_pc_closed_forest_evergreen_needle",
    "b2km_pc_closed_forest_forest_mixed",
    "b2km_pc_closed_forest_forest_other",
    "b2km_pc_closed_forest_forest_total",
    "b2km_pc_cultivated",
    "b2km_pc_herbaceous_vegetation",
    "b2km_pc_herbaceous_wetland",
    "b2km_pc_moss_and_lichen",
    "b2km_pc_ocean",
    "b2km_pc_open_forest_deciduous_broadleaf",
    "b2km_pc_open_forest_deciduous_needle",
    "b2km_pc_open_forest_evergreen_broadleaf",
    "b2km_pc_open_forest_evergreen_needle",
    "b2km_pc_open_forest_forest_mixed",
    "b2km_pc_open_forest_forest_other",
    "b2km_pc_open_forest_forest_total",
    "b2km_pc_permanent_water",
    "b2km_pc_shrubs",
    "b2km_pc_snow",
    "b2km_pc_unknown",
    "b2km_pc_urban",
    "b3km_avg_pop_density",
    "b3km_pc_bare",
    "b3km_pc_closed_forest_deciduous_broadleaf",
    "b3km_pc_closed_forest_deciduous_needle",
    "b3km_pc_closed_forest_evergreen_broadleaf",
    "b3km_pc_closed_forest_evergreen_needle",
    "b3km_pc_closed_forest_forest_mixed",
    "b3km_pc_closed_forest_forest_other",
    "b3km_pc_closed_forest_forest_total",
    "b3km_pc_cultivated",
    "b3km_pc_herbaceous_vegetation",
    "b3km_pc_herbaceous_wetland",
    "b3km_pc_moss_and_lichen",
    "b3km_pc_ocean",
    "b3km_pc_open_forest_deciduous_broadleaf",
    "b3km_pc_open_forest_deciduous_needle",
    "b3km_pc_open_forest_evergreen_broadleaf",
    "b3km_pc_open_forest_evergreen_needle",
    "b3km_pc_open_forest_forest_mixed",
    "b3km_pc_open_forest_forest_other",
    "b3km_pc_open_forest_forest_total",
    "b3km_pc_permanent_water",
    "b3km_pc_shrubs",
    "b3km_pc_snow",
    "b3km_pc_unknown",
    "b3km_pc_urban",
    "b4km_avg_pop_density",
    "b4km_pc_bare",
    "b4km_pc_closed_forest_deciduous_broadleaf",
    "b4km_pc_closed_forest_deciduous_needle",
    "b4km_pc_closed_forest_evergreen_broadleaf",
    "b4km_pc_closed_forest_evergreen_needle",
    "b4km_pc_closed_forest_forest_mixed",
    "b4km_pc_closed_forest_forest_other",
    "b4km_pc_closed_forest_forest_total",
    "b4km_pc_cultivated",
    "b4km_pc_herbaceous_vegetation",
    "b4km_pc_herbaceous_wetland",
    "b4km_pc_moss_and_lichen",
    "b4km_pc_ocean",
    "b4km_pc_open_forest_deciduous_broadleaf",
    "b4km_pc_open_forest_deciduous_needle",
    "b4km_pc_open_forest_evergreen_broadleaf",
    "b4km_pc_open_forest_evergreen_needle",
    "b4km_pc_open_forest_forest_mixed",
    "b4km_pc_open_forest_forest_other",
    "b4km_pc_open_forest_forest_total",
    "b4km_pc_permanent_water",
    "b4km_pc_shrubs",
    "b4km_pc_snow",
    "b4km_pc_unknown",
    "b4km_pc_urban",
    "b5km_avg_pop_density",
    "b5km_pc_bare",
    "b5km_pc_closed_forest_deciduous_broadleaf",
    "b5km_pc_closed_forest_deciduous_needle",
    "b5km_pc_closed_forest_evergreen_broadleaf",
    "b5km_pc_closed_forest_evergreen_needle",
    "b5km_pc_closed_forest_forest_mixed",
    "b5km_pc_closed_forest_forest_other",
    "b5km_pc_closed_forest_forest_total",
    "b5km_pc_cultivated",
    "b5km_pc_herbaceous_vegetation",
    "b5km_pc_herbaceous_wetland",
    "b5km_pc_moss_and_lichen",
    "b5km_pc_ocean",
    "b5km_pc_open_forest_deciduous_broadleaf",
    "b5km_pc_open_forest_deciduous_needle",
    "b5km_pc_open_forest_evergreen_broadleaf",
    "b5km_pc_open_forest_evergreen_needle",
    "b5km_pc_open_forest_forest_mixed",
    "b5km_pc_open_forest_forest_other",
    "b5km_pc_open_forest_forest_total",
    "b5km_pc_permanent_water",
    "b5km_pc_shrubs",
    "b5km_pc_snow",
    "b5km_pc_unknown",
    "b5km_pc_urban"
)]
```

```{r}
names(data[,-1])
```



```{r}
rf <- randomForest(
      locality_project_richness ~ .,
      data=data[,-1],
      ntree = 2000,
      replace = FALSE,
      importance = TRUE
    )
rf
```

```{r}
data.frame(t(randomForest::importance(rf, type = 1, scale = F)))
```

```{r}
grab_importance <- function(dataset) {
  rf <- randomForest(
      locality_project_richness ~ .,
      data=dataset,
      ntree = 2000,
      replace = FALSE,
      importance = TRUE
  )
  t(randomForest::importance(rf, type = 1, scale = F))
}
```


```{r}
test <- data.frame()
for (i in 1:50) {
    test = rbind(test, grab_importance(data[,-1]))
}
```


```{r}
sorted.test <- test[,order(colMeans(-test),colMeans(-test))]
sorted.test 
```


```{r}
ggplot(data = melt(sorted.test[,c(1:50)]), aes(x=variable, y=value)) + 
  geom_boxplot() + 
  xlab("Predictor Name") + ylab("Importance") +
  theme_bw() + theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

```{r}
sd.test <- data.frame(sapply(sorted.test, sd))
sd.test
```

```{r}
d <- sd.test
names <- rownames(d)
rownames(d) <- NULL
variable_selection_output <- cbind(names,d)
variable_selection_output
```

```{r}
sd.test$x <- c(1:211)
sd.test$y <- sd.test$sapply.sorted.test..sd.
sd.model <- rpart(y ~ x, data=sd.test)
sd.predict <- predict(sd.model)
sd.predict
```

0.01726565
```{r}
sd.test[c(1:20),]
```

```{r}
candidates <- sd.test[c(1:50),]
names2 <- rownames(candidates)

ggplot(data = candidates, aes(x=x, y=y)) + 
  geom_line() +
  ylab("Standard Deviation of VI") +
  xlab("Predictor Name") + scale_x_discrete(limits=names2) + 
  geom_hline(yintercept = 0.01726565 , linetype="dashed", color = "red") +
  theme_bw()  + theme(axis.text.x = element_text(angle = 90, hjust = 1))
```


```{r}
sd.test$keep <- sd.test$sapply.sorted.test..sd. >  0.01726565
sd.test[sd.test$keep == T,]
```
number_of_checklists
latitude
elevation
pop_2015

b500_pc_urban
b500_avg_pop_density
b500_pc_open_forest_forest_other
b500_pc_open_forest_forest_total
b1km_pc_shrubs
b500_pc_closed_forest_forest_total
b1km_pc_cultivated
b500_pc_herbaceous_wetland
b500_pc_closed_forest_forest_other
b500_pc_closed_forest_deciduous_broadleaf
b1km_pc_permanent_water
b3km_pc_herbaceous_vegetation
b5km_pc_bare
b5km_pc_closed_forest_evergreen_needle
b500_pc_ocean
b5km_pc_open_forest_evergreen_needle
b5km_pc_closed_forest_evergreen_broadleaf
b5km_pc_open_forest_deciduous_broadleaf
b5km_pc_closed_forest_forest_mixed
b5km_pc_open_forest_evergreen_broadleaf

city_pc_permanent_water
city_pc_urban
city_pc_cultivated
city_pc_shrubs
city_pc_closed_forest_evergreen_needle
city_pc_open_forest_forest_other
city_pc_open_forest_forest_total
city_pc_closed_forest_forest_other
city_pc_closed_forest_forest_total
city_pc_bare
city_pc_herbaceous_vegetation
city_pc_herbaceous_wetland
city_pc_closed_forest_deciduous_broadleaf
city_pc_closed_forest_forest_mixed
city_pc_open_forest_deciduous_broadleaf
city_pc_open_forest_evergreen_needle
city_pc_closed_forest_evergreen_broadleaf
city_pc_open_forest_evergreen_broadleaf
city_pc_ocean

region_pc_shrubs
region_pc_closed_forest_evergreen_needle
region_pc_cultivated
region_pc_open_forest_evergreen_needle
region_pc_closed_forest_forest_total
region_pc_permanent_water
region_pc_open_forest_forest_other
region_pc_bare
region_pc_herbaceous_wetland
region_pc_closed_forest_deciduous_broadleaf
region_pc_urban
region_pc_closed_forest_forest_other
region_pc_open_forest_deciduous_broadleaf
region_pc_closed_forest_evergreen_broadleaf
region_pc_open_forest_evergreen_broadleaf
region_pc_closed_forest_forest_mixed
region_pc_snow
region_pc_ocean
region_pc_open_forest_forest_mixed
region_pc_unknown

```{r}
data_reduced <- data[,c(
    "city_name",
    "locality_project_richness",
    "pop_2015",
    "number_of_checklists",
    "elevation",
    "latitude",
    "city_pc_permanent_water",
    "city_pc_urban",
    "city_pc_cultivated",
    "city_pc_shrubs",
    "city_pc_closed_forest_evergreen_needle",
    "city_pc_open_forest_forest_other",
    "city_pc_open_forest_forest_total",
    "city_pc_closed_forest_forest_other",
    "city_pc_closed_forest_forest_total",
    "city_pc_bare",
    "city_pc_herbaceous_vegetation",
    "city_pc_herbaceous_wetland",
    "city_pc_closed_forest_deciduous_broadleaf",
    "city_pc_closed_forest_forest_mixed",
    "city_pc_open_forest_deciduous_broadleaf",
    "city_pc_open_forest_evergreen_needle",
    "city_pc_closed_forest_evergreen_broadleaf",
    "city_pc_open_forest_evergreen_broadleaf",
    "city_pc_ocean",
    "region_pc_shrubs",
    "region_pc_closed_forest_evergreen_needle",
    "region_pc_cultivated",
    "region_pc_open_forest_evergreen_needle",
    "region_pc_closed_forest_forest_total",
    "region_pc_permanent_water",
    "region_pc_open_forest_forest_other",
    "region_pc_bare",
    "region_pc_herbaceous_wetland",
    "region_pc_closed_forest_deciduous_broadleaf",
    "region_pc_urban",
    "region_pc_closed_forest_forest_other",
    "region_pc_open_forest_deciduous_broadleaf",
    "region_pc_closed_forest_evergreen_broadleaf",
    "region_pc_open_forest_evergreen_broadleaf",
    "region_pc_closed_forest_forest_mixed",
    "region_pc_snow",
    "region_pc_ocean",
    "region_pc_open_forest_forest_mixed",
    "region_pc_unknown",
    "b500_pc_urban",
    "b500_avg_pop_density",
    "b500_pc_open_forest_forest_other",
    "b500_pc_open_forest_forest_total",
    "b1km_pc_shrubs",
    "b500_pc_closed_forest_forest_total",
    "b1km_pc_cultivated",
    "b500_pc_herbaceous_wetland",
    "b500_pc_closed_forest_forest_other",
    "b500_pc_closed_forest_deciduous_broadleaf",
    "b1km_pc_permanent_water",
    "b3km_pc_herbaceous_vegetation",
    "b5km_pc_bare",
    "b5km_pc_closed_forest_evergreen_needle",
    "b500_pc_ocean",
    "b5km_pc_open_forest_evergreen_needle",
    "b5km_pc_closed_forest_evergreen_broadleaf",
    "b5km_pc_open_forest_deciduous_broadleaf",
    "b5km_pc_closed_forest_forest_mixed",
    "b5km_pc_open_forest_evergreen_broadleaf"
)]
data_reduced[,-1]
```

```{r}
test_reduced <- data.frame()
for (i in 1:50) {
    test_reduced = nextimportance(test_reduced, data_reduced[,-1])
}
```


```{r}
sorted.test_reduced <- test_reduced[,order(colMeans(-test_reduced),colMeans(-test_reduced))]
sorted.test_reduced
```

```{r}
ggplot(data = melt(sorted.test_reduced), aes(x=variable, y=value)) + 
  geom_boxplot() + 
  xlab("Predictor Name") + ylab("Importance") +
  theme_bw() + theme(axis.text.x = element_text(angle = 90, hjust = 1))
```
```{r}
sd.test_reduced <- data.frame(sapply(sorted.test_reduced, sd))
sd.test_reduced
```

```{r}
d2 <- sd.test_reduced
names_r <- rownames(d2)
rownames(d2) <- NULL
variable_selection_output_r <- cbind(names_r,d2)
variable_selection_output_r
```
```{r}
sd.test_reduced$x <- c(1:63)
sd.test_reduced$y <- sd.test_reduced$sapply.sorted.test_reduced..sd.
sd.model_reduced <- rpart(y ~ x, data=sd.test_reduced)
sd.predict_r <- predict(sd.model_reduced)
sd.predict_r
```
0.2544938 
```{r}
ggplot(data = sd.test_reduced, aes(x=x, y=y)) + 
  geom_line() +
  ylab("Standard Deviation of VI") +
  xlab("Predictor Name") + scale_x_discrete(limits=names_r) + 
  geom_hline(yintercept = 0.09548451  , linetype="dashed", color = "red") +
  theme_bw()  + theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

```{r}
sd.test_reduced$keep <- sd.test_reduced$sapply.sorted.test_reduced..sd. >  0.09548451 
sd.test_reduced[sd.test_reduced$keep == T,]
```
```{r}
chosen <- row.names(sd.test_reduced)
write_lines(chosen, "chosen.txt")
```

```{r}
generate_oob <- function(data) {
    rf <- randomForest(
      locality_project_richness ~ .,
      data=data,
      replace = FALSE,
      importance = TRUE
    )
    mean(rf$mse)
}

create_fifty_rows_of_oob <- function(dataset) {
  result <- c()
  
  for (i in 1:50) {
    result <- append(result, generate_oob(dataset))
  }
  
  m <- mean(result)
  sd <- sd(result)
  sum <- m + sd
  c(m, sd, sum)
}
```

```{r}
rf <- randomForest(
      type = classification,
      locality_project_richness ~ .,
      data=data[,c("locality_project_richness", "b500_pc_urban")],
      replace = FALSE,
      importance = TRUE
    )
    mean(rf$mse)
    
```

```{r}
create_fifty_rows_of_oob(data[,c("locality_project_richness", "b500_pc_urban")])
create_fifty_rows_of_oob(data[,c("locality_project_richness", "b500_pc_urban", "b500_avg_pop_density")])
create_fifty_rows_of_oob(data[,c("locality_project_richness", "b500_pc_urban", "b500_avg_pop_density", "b500_pc_open_forest_forest_other")])
create_fifty_rows_of_oob(data[,c("locality_project_richness", "b500_pc_urban", "b500_avg_pop_density", "b500_pc_open_forest_forest_other", "b500_pc_open_forest_forest_total")])
create_fifty_rows_of_oob(data[,c("locality_project_richness", "b500_pc_urban", "b500_avg_pop_density", "b500_pc_open_forest_forest_other", "b500_pc_open_forest_forest_total", "region_pc_shrubs")])
create_fifty_rows_of_oob(data[,c("locality_project_richness", "b500_pc_urban", "b500_avg_pop_density", "b500_pc_open_forest_forest_other", "b500_pc_open_forest_forest_total", "region_pc_shrubs", "latitude")])
create_fifty_rows_of_oob(data[,c("locality_project_richness", "b500_pc_urban", "b500_avg_pop_density", "b500_pc_open_forest_forest_other", "b500_pc_open_forest_forest_total", "region_pc_shrubs", "latitude", "number_of_checklists")])
create_fifty_rows_of_oob(data[,c("locality_project_richness", "b500_pc_urban", "b500_avg_pop_density", "b500_pc_open_forest_forest_other", "b500_pc_open_forest_forest_total", "region_pc_shrubs", "latitude", "number_of_checklists", "b1km_pc_shrubs")])
create_fifty_rows_of_oob(data[,c("locality_project_richness", "b500_pc_urban", "b500_avg_pop_density", "b500_pc_open_forest_forest_other", "b500_pc_open_forest_forest_total", "region_pc_shrubs", "latitude", "number_of_checklists", "b1km_pc_shrubs", "b1km_pc_cultivated")])
create_fifty_rows_of_oob(data[,c("locality_project_richness", "b500_pc_urban", "b500_avg_pop_density", "b500_pc_open_forest_forest_other", "b500_pc_open_forest_forest_total", "region_pc_shrubs", "latitude", "number_of_checklists", "b1km_pc_shrubs", "b1km_pc_cultivated", "city_pc_permanent_water")])
create_fifty_rows_of_oob(data[,c("locality_project_richness", "b500_pc_urban", "b500_avg_pop_density", "b500_pc_open_forest_forest_other", "b500_pc_open_forest_forest_total", "region_pc_shrubs", "latitude", "number_of_checklists", "b1km_pc_shrubs", "b1km_pc_cultivated", "city_pc_permanent_water", "b500_pc_closed_forest_forest_total")])
create_fifty_rows_of_oob(data[,c("locality_project_richness", "b500_pc_urban", "b500_avg_pop_density", "b500_pc_open_forest_forest_other", "b500_pc_open_forest_forest_total", "region_pc_shrubs", "latitude", "number_of_checklists", "b1km_pc_shrubs", "b1km_pc_cultivated", "city_pc_permanent_water", "b500_pc_closed_forest_forest_total", "b500_pc_herbaceous_wetland")])
create_fifty_rows_of_oob(data[,c("locality_project_richness", "b500_pc_urban", "b500_avg_pop_density", "b500_pc_open_forest_forest_other", "b500_pc_open_forest_forest_total", "region_pc_shrubs", "latitude", "number_of_checklists", "b1km_pc_shrubs", "b1km_pc_cultivated", "city_pc_permanent_water", "b500_pc_closed_forest_forest_total", "b500_pc_herbaceous_wetland", "b3km_pc_herbaceous_vegetation")])
create_fifty_rows_of_oob(data[,c("locality_project_richness", "b500_pc_urban", "b500_avg_pop_density", "b500_pc_open_forest_forest_other", "b500_pc_open_forest_forest_total", "region_pc_shrubs", "latitude", "number_of_checklists", "b1km_pc_shrubs", "b1km_pc_cultivated", "city_pc_permanent_water", "b500_pc_closed_forest_forest_total", "b500_pc_herbaceous_wetland", "b3km_pc_herbaceous_vegetation", "city_pc_cultivated")])
create_fifty_rows_of_oob(data[,c("locality_project_richness", "b500_pc_urban", "b500_avg_pop_density", "b500_pc_open_forest_forest_other", "b500_pc_open_forest_forest_total", "region_pc_shrubs", "latitude", "number_of_checklists", "b1km_pc_shrubs", "b1km_pc_cultivated", "city_pc_permanent_water", "b500_pc_closed_forest_forest_total", "b500_pc_herbaceous_wetland", "b3km_pc_herbaceous_vegetation", "city_pc_cultivated", "city_pc_shrubs")])
create_fifty_rows_of_oob(data[,c("locality_project_richness", "b500_pc_urban", "b500_avg_pop_density", "b500_pc_open_forest_forest_other", "b500_pc_open_forest_forest_total", "region_pc_shrubs", "latitude", "number_of_checklists", "b1km_pc_shrubs", "b1km_pc_cultivated", "city_pc_permanent_water", "b500_pc_closed_forest_forest_total", "b500_pc_herbaceous_wetland", "b3km_pc_herbaceous_vegetation", "city_pc_cultivated", "city_pc_shrubs", "b500_pc_closed_forest_forest_other")])
create_fifty_rows_of_oob(data[,c("locality_project_richness", "b500_pc_urban", "b500_avg_pop_density", "b500_pc_open_forest_forest_other", "b500_pc_open_forest_forest_total", "region_pc_shrubs", "latitude", "number_of_checklists", "b1km_pc_shrubs", "b1km_pc_cultivated", "city_pc_permanent_water", "b500_pc_closed_forest_forest_total", "b500_pc_herbaceous_wetland", "b3km_pc_herbaceous_vegetation", "city_pc_cultivated", "city_pc_shrubs", "b500_pc_closed_forest_forest_other", "city_pc_urban")])
create_fifty_rows_of_oob(data[,c("locality_project_richness", "b500_pc_urban", "b500_avg_pop_density", "b500_pc_open_forest_forest_other", "b500_pc_open_forest_forest_total", "region_pc_shrubs", "latitude", "number_of_checklists", "b1km_pc_shrubs", "b1km_pc_cultivated", "city_pc_permanent_water", "b500_pc_closed_forest_forest_total", "b500_pc_herbaceous_wetland", "b3km_pc_herbaceous_vegetation", "city_pc_cultivated", "city_pc_shrubs", "b500_pc_closed_forest_forest_other", "city_pc_urban", "region_pc_cultivated")])
create_fifty_rows_of_oob(data[,c("locality_project_richness", "b500_pc_urban", "b500_avg_pop_density", "b500_pc_open_forest_forest_other", "b500_pc_open_forest_forest_total", "region_pc_shrubs", "latitude", "number_of_checklists", "b1km_pc_shrubs", "b1km_pc_cultivated", "city_pc_permanent_water", "b500_pc_closed_forest_forest_total", "b500_pc_herbaceous_wetland", "b3km_pc_herbaceous_vegetation", "city_pc_cultivated", "city_pc_shrubs", "b500_pc_closed_forest_forest_other", "city_pc_urban", "region_pc_cultivated", "b1km_pc_permanent_water")])
create_fifty_rows_of_oob(data[,c("locality_project_richness", "b500_pc_urban", "b500_avg_pop_density", "b500_pc_open_forest_forest_other", "b500_pc_open_forest_forest_total", "region_pc_shrubs", "latitude", "number_of_checklists", "b1km_pc_shrubs", "b1km_pc_cultivated", "city_pc_permanent_water", "b500_pc_closed_forest_forest_total", "b500_pc_herbaceous_wetland", "b3km_pc_herbaceous_vegetation", "city_pc_cultivated", "city_pc_shrubs", "b500_pc_closed_forest_forest_other", "city_pc_urban", "region_pc_cultivated", "b1km_pc_permanent_water", "b5km_pc_bare")])
create_fifty_rows_of_oob(data[,c("locality_project_richness", "b500_pc_urban", "b500_avg_pop_density", "b500_pc_open_forest_forest_other", "b500_pc_open_forest_forest_total", "region_pc_shrubs", "latitude", "number_of_checklists", "b1km_pc_shrubs", "b1km_pc_cultivated", "city_pc_permanent_water", "b500_pc_closed_forest_forest_total", "b500_pc_herbaceous_wetland", "b3km_pc_herbaceous_vegetation", "city_pc_cultivated", "city_pc_shrubs", "b500_pc_closed_forest_forest_other", "city_pc_urban", "region_pc_cultivated", "b1km_pc_permanent_water", "b5km_pc_bare", "region_pc_closed_forest_evergreen_needle")])
create_fifty_rows_of_oob(data[,c("locality_project_richness", "b500_pc_urban", "b500_avg_pop_density", "b500_pc_open_forest_forest_other", "b500_pc_open_forest_forest_total", "region_pc_shrubs", "latitude", "number_of_checklists", "b1km_pc_shrubs", "b1km_pc_cultivated", "city_pc_permanent_water", "b500_pc_closed_forest_forest_total", "b500_pc_herbaceous_wetland", "b3km_pc_herbaceous_vegetation", "city_pc_cultivated", "city_pc_shrubs", "b500_pc_closed_forest_forest_other", "city_pc_urban", "region_pc_cultivated", "b1km_pc_permanent_water", "b5km_pc_bare", "region_pc_closed_forest_evergreen_needle", "elevation")])
create_fifty_rows_of_oob(data[,c("locality_project_richness", "b500_pc_urban", "b500_avg_pop_density", "b500_pc_open_forest_forest_other", "b500_pc_open_forest_forest_total", "region_pc_shrubs", "latitude", "number_of_checklists", "b1km_pc_shrubs", "b1km_pc_cultivated", "city_pc_permanent_water", "b500_pc_closed_forest_forest_total", "b500_pc_herbaceous_wetland", "b3km_pc_herbaceous_vegetation", "city_pc_cultivated", "city_pc_shrubs", "b500_pc_closed_forest_forest_other", "city_pc_urban", "region_pc_cultivated", "b1km_pc_permanent_water", "b5km_pc_bare", "region_pc_closed_forest_evergreen_needle", "elevation", "region_pc_closed_forest_forest_total")])
create_fifty_rows_of_oob(data[,c("locality_project_richness", "b500_pc_urban", "b500_avg_pop_density", "b500_pc_open_forest_forest_other", "b500_pc_open_forest_forest_total", "region_pc_shrubs", "latitude", "number_of_checklists", "b1km_pc_shrubs", "b1km_pc_cultivated", "city_pc_permanent_water", "b500_pc_closed_forest_forest_total", "b500_pc_herbaceous_wetland", "b3km_pc_herbaceous_vegetation", "city_pc_cultivated", "city_pc_shrubs", "b500_pc_closed_forest_forest_other", "city_pc_urban", "region_pc_cultivated", "b1km_pc_permanent_water", "b5km_pc_bare", "region_pc_closed_forest_evergreen_needle", "elevation", "region_pc_closed_forest_forest_total", "region_pc_open_forest_evergreen_needle")])
create_fifty_rows_of_oob(data[,c("locality_project_richness", "b500_pc_urban", "b500_avg_pop_density", "b500_pc_open_forest_forest_other", "b500_pc_open_forest_forest_total", "region_pc_shrubs", "latitude", "number_of_checklists", "b1km_pc_shrubs", "b1km_pc_cultivated", "city_pc_permanent_water", "b500_pc_closed_forest_forest_total", "b500_pc_herbaceous_wetland", "b3km_pc_herbaceous_vegetation", "city_pc_cultivated", "city_pc_shrubs", "b500_pc_closed_forest_forest_other", "city_pc_urban", "region_pc_cultivated", "b1km_pc_permanent_water", "b5km_pc_bare", "region_pc_closed_forest_evergreen_needle", "elevation", "region_pc_closed_forest_forest_total", "region_pc_open_forest_evergreen_needle", "b5km_pc_closed_forest_evergreen_needle")])
create_fifty_rows_of_oob(data[,c("locality_project_richness", "b500_pc_urban", "b500_avg_pop_density", "b500_pc_open_forest_forest_other", "b500_pc_open_forest_forest_total", "region_pc_shrubs", "latitude", "number_of_checklists", "b1km_pc_shrubs", "b1km_pc_cultivated", "city_pc_permanent_water", "b500_pc_closed_forest_forest_total", "b500_pc_herbaceous_wetland", "b3km_pc_herbaceous_vegetation", "city_pc_cultivated", "city_pc_shrubs", "b500_pc_closed_forest_forest_other", "city_pc_urban", "region_pc_cultivated", "b1km_pc_permanent_water", "b5km_pc_bare", "region_pc_closed_forest_evergreen_needle", "elevation", "region_pc_closed_forest_forest_total", "region_pc_open_forest_evergreen_needle", "b5km_pc_closed_forest_evergreen_needle", "city_pc_closed_forest_evergreen_needle")])
create_fifty_rows_of_oob(data[,c("locality_project_richness", "b500_pc_urban", "b500_avg_pop_density", "b500_pc_open_forest_forest_other", "b500_pc_open_forest_forest_total", "region_pc_shrubs", "latitude", "number_of_checklists", "b1km_pc_shrubs", "b1km_pc_cultivated", "city_pc_permanent_water", "b500_pc_closed_forest_forest_total", "b500_pc_herbaceous_wetland", "b3km_pc_herbaceous_vegetation", "city_pc_cultivated", "city_pc_shrubs", "b500_pc_closed_forest_forest_other", "city_pc_urban", "region_pc_cultivated", "b1km_pc_permanent_water", "b5km_pc_bare", "region_pc_closed_forest_evergreen_needle", "elevation", "region_pc_closed_forest_forest_total", "region_pc_open_forest_evergreen_needle", "b5km_pc_closed_forest_evergreen_needle", "city_pc_closed_forest_evergreen_needle", "b500_pc_closed_forest_deciduous_broadleaf")])
create_fifty_rows_of_oob(data[,c("locality_project_richness", "b500_pc_urban", "b500_avg_pop_density", "b500_pc_open_forest_forest_other", "b500_pc_open_forest_forest_total", "region_pc_shrubs", "latitude", "number_of_checklists", "b1km_pc_shrubs", "b1km_pc_cultivated", "city_pc_permanent_water", "b500_pc_closed_forest_forest_total", "b500_pc_herbaceous_wetland", "b3km_pc_herbaceous_vegetation", "city_pc_cultivated", "city_pc_shrubs", "b500_pc_closed_forest_forest_other", "city_pc_urban", "region_pc_cultivated", "b1km_pc_permanent_water", "b5km_pc_bare", "region_pc_closed_forest_evergreen_needle", "elevation", "region_pc_closed_forest_forest_total", "region_pc_open_forest_evergreen_needle", "b5km_pc_closed_forest_evergreen_needle", "city_pc_closed_forest_evergreen_needle", "b500_pc_closed_forest_deciduous_broadleaf", "region_pc_permanent_water")])
create_fifty_rows_of_oob(data[,c("locality_project_richness", "b500_pc_urban", "b500_avg_pop_density", "b500_pc_open_forest_forest_other", "b500_pc_open_forest_forest_total", "region_pc_shrubs", "latitude", "number_of_checklists", "b1km_pc_shrubs", "b1km_pc_cultivated", "city_pc_permanent_water", "b500_pc_closed_forest_forest_total", "b500_pc_herbaceous_wetland", "b3km_pc_herbaceous_vegetation", "city_pc_cultivated", "city_pc_shrubs", "b500_pc_closed_forest_forest_other", "city_pc_urban", "region_pc_cultivated", "b1km_pc_permanent_water", "b5km_pc_bare", "region_pc_closed_forest_evergreen_needle", "elevation", "region_pc_closed_forest_forest_total", "region_pc_open_forest_evergreen_needle", "b5km_pc_closed_forest_evergreen_needle", "city_pc_closed_forest_evergreen_needle", "b500_pc_closed_forest_deciduous_broadleaf", "region_pc_permanent_water", "region_pc_open_forest_forest_other")])
create_fifty_rows_of_oob(data[,c("locality_project_richness", "b500_pc_urban", "b500_avg_pop_density", "b500_pc_open_forest_forest_other", "b500_pc_open_forest_forest_total", "region_pc_shrubs", "latitude", "number_of_checklists", "b1km_pc_shrubs", "b1km_pc_cultivated", "city_pc_permanent_water", "b500_pc_closed_forest_forest_total", "b500_pc_herbaceous_wetland", "b3km_pc_herbaceous_vegetation", "city_pc_cultivated", "city_pc_shrubs", "b500_pc_closed_forest_forest_other", "city_pc_urban", "region_pc_cultivated", "b1km_pc_permanent_water", "b5km_pc_bare", "region_pc_closed_forest_evergreen_needle", "elevation", "region_pc_closed_forest_forest_total", "region_pc_open_forest_evergreen_needle", "b5km_pc_closed_forest_evergreen_needle", "city_pc_closed_forest_evergreen_needle", "b500_pc_closed_forest_deciduous_broadleaf", "region_pc_permanent_water", "region_pc_open_forest_forest_other", "b500_pc_ocean")])
create_fifty_rows_of_oob(data[,c("locality_project_richness", "b500_pc_urban", "b500_avg_pop_density", "b500_pc_open_forest_forest_other", "b500_pc_open_forest_forest_total", "region_pc_shrubs", "latitude", "number_of_checklists", "b1km_pc_shrubs", "b1km_pc_cultivated", "city_pc_permanent_water", "b500_pc_closed_forest_forest_total", "b500_pc_herbaceous_wetland", "b3km_pc_herbaceous_vegetation", "city_pc_cultivated", "city_pc_shrubs", "b500_pc_closed_forest_forest_other", "city_pc_urban", "region_pc_cultivated", "b1km_pc_permanent_water", "b5km_pc_bare", "region_pc_closed_forest_evergreen_needle", "elevation", "region_pc_closed_forest_forest_total", "region_pc_open_forest_evergreen_needle", "b5km_pc_closed_forest_evergreen_needle", "city_pc_closed_forest_evergreen_needle", "b500_pc_closed_forest_deciduous_broadleaf", "region_pc_permanent_water", "region_pc_open_forest_forest_other", "b500_pc_ocean", "city_pc_open_forest_forest_total")])
create_fifty_rows_of_oob(data[,c("locality_project_richness", "b500_pc_urban", "b500_avg_pop_density", "b500_pc_open_forest_forest_other", "b500_pc_open_forest_forest_total", "region_pc_shrubs", "latitude", "number_of_checklists", "b1km_pc_shrubs", "b1km_pc_cultivated", "city_pc_permanent_water", "b500_pc_closed_forest_forest_total", "b500_pc_herbaceous_wetland", "b3km_pc_herbaceous_vegetation", "city_pc_cultivated", "city_pc_shrubs", "b500_pc_closed_forest_forest_other", "city_pc_urban", "region_pc_cultivated", "b1km_pc_permanent_water", "b5km_pc_bare", "region_pc_closed_forest_evergreen_needle", "elevation", "region_pc_closed_forest_forest_total", "region_pc_open_forest_evergreen_needle", "b5km_pc_closed_forest_evergreen_needle", "city_pc_closed_forest_evergreen_needle", "b500_pc_closed_forest_deciduous_broadleaf", "region_pc_permanent_water", "region_pc_open_forest_forest_other", "b500_pc_ocean", "city_pc_open_forest_forest_total", "city_pc_bare")])
create_fifty_rows_of_oob(data[,c("locality_project_richness", "b500_pc_urban", "b500_avg_pop_density", "b500_pc_open_forest_forest_other", "b500_pc_open_forest_forest_total", "region_pc_shrubs", "latitude", "number_of_checklists", "b1km_pc_shrubs", "b1km_pc_cultivated", "city_pc_permanent_water", "b500_pc_closed_forest_forest_total", "b500_pc_herbaceous_wetland", "b3km_pc_herbaceous_vegetation", "city_pc_cultivated", "city_pc_shrubs", "b500_pc_closed_forest_forest_other", "city_pc_urban", "region_pc_cultivated", "b1km_pc_permanent_water", "b5km_pc_bare", "region_pc_closed_forest_evergreen_needle", "elevation", "region_pc_closed_forest_forest_total", "region_pc_open_forest_evergreen_needle", "b5km_pc_closed_forest_evergreen_needle", "city_pc_closed_forest_evergreen_needle", "b500_pc_closed_forest_deciduous_broadleaf", "region_pc_permanent_water", "region_pc_open_forest_forest_other", "b500_pc_ocean", "city_pc_open_forest_forest_total", "city_pc_bare", "region_pc_bare")])
create_fifty_rows_of_oob(data[,c("locality_project_richness", "b500_pc_urban", "b500_avg_pop_density", "b500_pc_open_forest_forest_other", "b500_pc_open_forest_forest_total", "region_pc_shrubs", "latitude", "number_of_checklists", "b1km_pc_shrubs", "b1km_pc_cultivated", "city_pc_permanent_water", "b500_pc_closed_forest_forest_total", "b500_pc_herbaceous_wetland", "b3km_pc_herbaceous_vegetation", "city_pc_cultivated", "city_pc_shrubs", "b500_pc_closed_forest_forest_other", "city_pc_urban", "region_pc_cultivated", "b1km_pc_permanent_water", "b5km_pc_bare", "region_pc_closed_forest_evergreen_needle", "elevation", "region_pc_closed_forest_forest_total", "region_pc_open_forest_evergreen_needle", "b5km_pc_closed_forest_evergreen_needle", "city_pc_closed_forest_evergreen_needle", "b500_pc_closed_forest_deciduous_broadleaf", "region_pc_permanent_water", "region_pc_open_forest_forest_other", "b500_pc_ocean", "city_pc_open_forest_forest_total", "city_pc_bare", "region_pc_bare", "city_pc_open_forest_forest_other")])
create_fifty_rows_of_oob(data[,c("locality_project_richness", "b500_pc_urban", "b500_avg_pop_density", "b500_pc_open_forest_forest_other", "b500_pc_open_forest_forest_total", "region_pc_shrubs", "latitude", "number_of_checklists", "b1km_pc_shrubs", "b1km_pc_cultivated", "city_pc_permanent_water", "b500_pc_closed_forest_forest_total", "b500_pc_herbaceous_wetland", "b3km_pc_herbaceous_vegetation", "city_pc_cultivated", "city_pc_shrubs", "b500_pc_closed_forest_forest_other", "city_pc_urban", "region_pc_cultivated", "b1km_pc_permanent_water", "b5km_pc_bare", "region_pc_closed_forest_evergreen_needle", "elevation", "region_pc_closed_forest_forest_total", "region_pc_open_forest_evergreen_needle", "b5km_pc_closed_forest_evergreen_needle", "city_pc_closed_forest_evergreen_needle", "b500_pc_closed_forest_deciduous_broadleaf", "region_pc_permanent_water", "region_pc_open_forest_forest_other", "b500_pc_ocean", "city_pc_open_forest_forest_total", "city_pc_bare", "region_pc_bare", "city_pc_open_forest_forest_other", "city_pc_closed_forest_forest_total")])
create_fifty_rows_of_oob(data[,c("locality_project_richness", "b500_pc_urban", "b500_avg_pop_density", "b500_pc_open_forest_forest_other", "b500_pc_open_forest_forest_total", "region_pc_shrubs", "latitude", "number_of_checklists", "b1km_pc_shrubs", "b1km_pc_cultivated", "city_pc_permanent_water", "b500_pc_closed_forest_forest_total", "b500_pc_herbaceous_wetland", "b3km_pc_herbaceous_vegetation", "city_pc_cultivated", "city_pc_shrubs", "b500_pc_closed_forest_forest_other", "city_pc_urban", "region_pc_cultivated", "b1km_pc_permanent_water", "b5km_pc_bare", "region_pc_closed_forest_evergreen_needle", "elevation", "region_pc_closed_forest_forest_total", "region_pc_open_forest_evergreen_needle", "b5km_pc_closed_forest_evergreen_needle", "city_pc_closed_forest_evergreen_needle", "b500_pc_closed_forest_deciduous_broadleaf", "region_pc_permanent_water", "region_pc_open_forest_forest_other", "b500_pc_ocean", "city_pc_open_forest_forest_total", "city_pc_bare", "region_pc_bare", "city_pc_open_forest_forest_other", "city_pc_closed_forest_forest_total", "city_pc_closed_forest_forest_other")])
create_fifty_rows_of_oob(data[,c("locality_project_richness", "b500_pc_urban", "b500_avg_pop_density", "b500_pc_open_forest_forest_other", "b500_pc_open_forest_forest_total", "region_pc_shrubs", "latitude", "number_of_checklists", "b1km_pc_shrubs", "b1km_pc_cultivated", "city_pc_permanent_water", "b500_pc_closed_forest_forest_total", "b500_pc_herbaceous_wetland", "b3km_pc_herbaceous_vegetation", "city_pc_cultivated", "city_pc_shrubs", "b500_pc_closed_forest_forest_other", "city_pc_urban", "region_pc_cultivated", "b1km_pc_permanent_water", "b5km_pc_bare", "region_pc_closed_forest_evergreen_needle", "elevation", "region_pc_closed_forest_forest_total", "region_pc_open_forest_evergreen_needle", "b5km_pc_closed_forest_evergreen_needle", "city_pc_closed_forest_evergreen_needle", "b500_pc_closed_forest_deciduous_broadleaf", "region_pc_permanent_water", "region_pc_open_forest_forest_other", "b500_pc_ocean", "city_pc_open_forest_forest_total", "city_pc_bare", "region_pc_bare", "city_pc_open_forest_forest_other", "city_pc_closed_forest_forest_total", "city_pc_closed_forest_forest_other", "region_pc_herbaceous_wetland")])
create_fifty_rows_of_oob(data[,c("locality_project_richness", "b500_pc_urban", "b500_avg_pop_density", "b500_pc_open_forest_forest_other", "b500_pc_open_forest_forest_total", "region_pc_shrubs", "latitude", "number_of_checklists", "b1km_pc_shrubs", "b1km_pc_cultivated", "city_pc_permanent_water", "b500_pc_closed_forest_forest_total", "b500_pc_herbaceous_wetland", "b3km_pc_herbaceous_vegetation", "city_pc_cultivated", "city_pc_shrubs", "b500_pc_closed_forest_forest_other", "city_pc_urban", "region_pc_cultivated", "b1km_pc_permanent_water", "b5km_pc_bare", "region_pc_closed_forest_evergreen_needle", "elevation", "region_pc_closed_forest_forest_total", "region_pc_open_forest_evergreen_needle", "b5km_pc_closed_forest_evergreen_needle", "city_pc_closed_forest_evergreen_needle", "b500_pc_closed_forest_deciduous_broadleaf", "region_pc_permanent_water", "region_pc_open_forest_forest_other", "b500_pc_ocean", "city_pc_open_forest_forest_total", "city_pc_bare", "region_pc_bare", "city_pc_open_forest_forest_other", "city_pc_closed_forest_forest_total", "city_pc_closed_forest_forest_other", "region_pc_herbaceous_wetland", "region_pc_closed_forest_deciduous_broadleaf")])
create_fifty_rows_of_oob(data[,c("locality_project_richness", "b500_pc_urban", "b500_avg_pop_density", "b500_pc_open_forest_forest_other", "b500_pc_open_forest_forest_total", "region_pc_shrubs", "latitude", "number_of_checklists", "b1km_pc_shrubs", "b1km_pc_cultivated", "city_pc_permanent_water", "b500_pc_closed_forest_forest_total", "b500_pc_herbaceous_wetland", "b3km_pc_herbaceous_vegetation", "city_pc_cultivated", "city_pc_shrubs", "b500_pc_closed_forest_forest_other", "city_pc_urban", "region_pc_cultivated", "b1km_pc_permanent_water", "b5km_pc_bare", "region_pc_closed_forest_evergreen_needle", "elevation", "region_pc_closed_forest_forest_total", "region_pc_open_forest_evergreen_needle", "b5km_pc_closed_forest_evergreen_needle", "city_pc_closed_forest_evergreen_needle", "b500_pc_closed_forest_deciduous_broadleaf", "region_pc_permanent_water", "region_pc_open_forest_forest_other", "b500_pc_ocean", "city_pc_open_forest_forest_total", "city_pc_bare", "region_pc_bare", "city_pc_open_forest_forest_other", "city_pc_closed_forest_forest_total", "city_pc_closed_forest_forest_other", "region_pc_herbaceous_wetland", "region_pc_closed_forest_deciduous_broadleaf", "region_pc_urban")])
create_fifty_rows_of_oob(data[,c("locality_project_richness", "b500_pc_urban", "b500_avg_pop_density", "b500_pc_open_forest_forest_other", "b500_pc_open_forest_forest_total", "region_pc_shrubs", "latitude", "number_of_checklists", "b1km_pc_shrubs", "b1km_pc_cultivated", "city_pc_permanent_water", "b500_pc_closed_forest_forest_total", "b500_pc_herbaceous_wetland", "b3km_pc_herbaceous_vegetation", "city_pc_cultivated", "city_pc_shrubs", "b500_pc_closed_forest_forest_other", "city_pc_urban", "region_pc_cultivated", "b1km_pc_permanent_water", "b5km_pc_bare", "region_pc_closed_forest_evergreen_needle", "elevation", "region_pc_closed_forest_forest_total", "region_pc_open_forest_evergreen_needle", "b5km_pc_closed_forest_evergreen_needle", "city_pc_closed_forest_evergreen_needle", "b500_pc_closed_forest_deciduous_broadleaf", "region_pc_permanent_water", "region_pc_open_forest_forest_other", "b500_pc_ocean", "city_pc_open_forest_forest_total", "city_pc_bare", "region_pc_bare", "city_pc_open_forest_forest_other", "city_pc_closed_forest_forest_total", "city_pc_closed_forest_forest_other", "region_pc_herbaceous_wetland", "region_pc_closed_forest_deciduous_broadleaf", "region_pc_urban", "city_pc_herbaceous_wetland")])
create_fifty_rows_of_oob(data[,c("locality_project_richness", "b500_pc_urban", "b500_avg_pop_density", "b500_pc_open_forest_forest_other", "b500_pc_open_forest_forest_total", "region_pc_shrubs", "latitude", "number_of_checklists", "b1km_pc_shrubs", "b1km_pc_cultivated", "city_pc_permanent_water", "b500_pc_closed_forest_forest_total", "b500_pc_herbaceous_wetland", "b3km_pc_herbaceous_vegetation", "city_pc_cultivated", "city_pc_shrubs", "b500_pc_closed_forest_forest_other", "city_pc_urban", "region_pc_cultivated", "b1km_pc_permanent_water", "b5km_pc_bare", "region_pc_closed_forest_evergreen_needle", "elevation", "region_pc_closed_forest_forest_total", "region_pc_open_forest_evergreen_needle", "b5km_pc_closed_forest_evergreen_needle", "city_pc_closed_forest_evergreen_needle", "b500_pc_closed_forest_deciduous_broadleaf", "region_pc_permanent_water", "region_pc_open_forest_forest_other", "b500_pc_ocean", "city_pc_open_forest_forest_total", "city_pc_bare", "region_pc_bare", "city_pc_open_forest_forest_other", "city_pc_closed_forest_forest_total", "city_pc_closed_forest_forest_other", "region_pc_herbaceous_wetland", "region_pc_closed_forest_deciduous_broadleaf", "region_pc_urban", "city_pc_herbaceous_wetland", "pop_2015")])
create_fifty_rows_of_oob(data[,c("locality_project_richness", "b500_pc_urban", "b500_avg_pop_density", "b500_pc_open_forest_forest_other", "b500_pc_open_forest_forest_total", "region_pc_shrubs", "latitude", "number_of_checklists", "b1km_pc_shrubs", "b1km_pc_cultivated", "city_pc_permanent_water", "b500_pc_closed_forest_forest_total", "b500_pc_herbaceous_wetland", "b3km_pc_herbaceous_vegetation", "city_pc_cultivated", "city_pc_shrubs", "b500_pc_closed_forest_forest_other", "city_pc_urban", "region_pc_cultivated", "b1km_pc_permanent_water", "b5km_pc_bare", "region_pc_closed_forest_evergreen_needle", "elevation", "region_pc_closed_forest_forest_total", "region_pc_open_forest_evergreen_needle", "b5km_pc_closed_forest_evergreen_needle", "city_pc_closed_forest_evergreen_needle", "b500_pc_closed_forest_deciduous_broadleaf", "region_pc_permanent_water", "region_pc_open_forest_forest_other", "b500_pc_ocean", "city_pc_open_forest_forest_total", "city_pc_bare", "region_pc_bare", "city_pc_open_forest_forest_other", "city_pc_closed_forest_forest_total", "city_pc_closed_forest_forest_other", "region_pc_herbaceous_wetland", "region_pc_closed_forest_deciduous_broadleaf", "region_pc_urban", "city_pc_herbaceous_wetland", "pop_2015", "region_pc_closed_forest_forest_other")])
create_fifty_rows_of_oob(data[,c("locality_project_richness", "b500_pc_urban", "b500_avg_pop_density", "b500_pc_open_forest_forest_other", "b500_pc_open_forest_forest_total", "region_pc_shrubs", "latitude", "number_of_checklists", "b1km_pc_shrubs", "b1km_pc_cultivated", "city_pc_permanent_water", "b500_pc_closed_forest_forest_total", "b500_pc_herbaceous_wetland", "b3km_pc_herbaceous_vegetation", "city_pc_cultivated", "city_pc_shrubs", "b500_pc_closed_forest_forest_other", "city_pc_urban", "region_pc_cultivated", "b1km_pc_permanent_water", "b5km_pc_bare", "region_pc_closed_forest_evergreen_needle", "elevation", "region_pc_closed_forest_forest_total", "region_pc_open_forest_evergreen_needle", "b5km_pc_closed_forest_evergreen_needle", "city_pc_closed_forest_evergreen_needle", "b500_pc_closed_forest_deciduous_broadleaf", "region_pc_permanent_water", "region_pc_open_forest_forest_other", "b500_pc_ocean", "city_pc_open_forest_forest_total", "city_pc_bare", "region_pc_bare", "city_pc_open_forest_forest_other", "city_pc_closed_forest_forest_total", "city_pc_closed_forest_forest_other", "region_pc_herbaceous_wetland", "region_pc_closed_forest_deciduous_broadleaf", "region_pc_urban", "city_pc_herbaceous_wetland", "pop_2015", "region_pc_closed_forest_forest_other", "city_pc_herbaceous_vegetation")])
create_fifty_rows_of_oob(data[,c("locality_project_richness", "b500_pc_urban", "b500_avg_pop_density", "b500_pc_open_forest_forest_other", "b500_pc_open_forest_forest_total", "region_pc_shrubs", "latitude", "number_of_checklists", "b1km_pc_shrubs", "b1km_pc_cultivated", "city_pc_permanent_water", "b500_pc_closed_forest_forest_total", "b500_pc_herbaceous_wetland", "b3km_pc_herbaceous_vegetation", "city_pc_cultivated", "city_pc_shrubs", "b500_pc_closed_forest_forest_other", "city_pc_urban", "region_pc_cultivated", "b1km_pc_permanent_water", "b5km_pc_bare", "region_pc_closed_forest_evergreen_needle", "elevation", "region_pc_closed_forest_forest_total", "region_pc_open_forest_evergreen_needle", "b5km_pc_closed_forest_evergreen_needle", "city_pc_closed_forest_evergreen_needle", "b500_pc_closed_forest_deciduous_broadleaf", "region_pc_permanent_water", "region_pc_open_forest_forest_other", "b500_pc_ocean", "city_pc_open_forest_forest_total", "city_pc_bare", "region_pc_bare", "city_pc_open_forest_forest_other", "city_pc_closed_forest_forest_total", "city_pc_closed_forest_forest_other", "region_pc_herbaceous_wetland", "region_pc_closed_forest_deciduous_broadleaf", "region_pc_urban", "city_pc_herbaceous_wetland", "pop_2015", "region_pc_closed_forest_forest_other", "city_pc_herbaceous_vegetation", "region_pc_closed_forest_evergreen_broadleaf")])
create_fifty_rows_of_oob(data[,c("locality_project_richness", "b500_pc_urban", "b500_avg_pop_density", "b500_pc_open_forest_forest_other", "b500_pc_open_forest_forest_total", "region_pc_shrubs", "latitude", "number_of_checklists", "b1km_pc_shrubs", "b1km_pc_cultivated", "city_pc_permanent_water", "b500_pc_closed_forest_forest_total", "b500_pc_herbaceous_wetland", "b3km_pc_herbaceous_vegetation", "city_pc_cultivated", "city_pc_shrubs", "b500_pc_closed_forest_forest_other", "city_pc_urban", "region_pc_cultivated", "b1km_pc_permanent_water", "b5km_pc_bare", "region_pc_closed_forest_evergreen_needle", "elevation", "region_pc_closed_forest_forest_total", "region_pc_open_forest_evergreen_needle", "b5km_pc_closed_forest_evergreen_needle", "city_pc_closed_forest_evergreen_needle", "b500_pc_closed_forest_deciduous_broadleaf", "region_pc_permanent_water", "region_pc_open_forest_forest_other", "b500_pc_ocean", "city_pc_open_forest_forest_total", "city_pc_bare", "region_pc_bare", "city_pc_open_forest_forest_other", "city_pc_closed_forest_forest_total", "city_pc_closed_forest_forest_other", "region_pc_herbaceous_wetland", "region_pc_closed_forest_deciduous_broadleaf", "region_pc_urban", "city_pc_herbaceous_wetland", "pop_2015", "region_pc_closed_forest_forest_other", "city_pc_herbaceous_vegetation", "region_pc_closed_forest_evergreen_broadleaf", "region_pc_open_forest_deciduous_broadleaf")])
create_fifty_rows_of_oob(data[,c("locality_project_richness", "b500_pc_urban", "b500_avg_pop_density", "b500_pc_open_forest_forest_other", "b500_pc_open_forest_forest_total", "region_pc_shrubs", "latitude", "number_of_checklists", "b1km_pc_shrubs", "b1km_pc_cultivated", "city_pc_permanent_water", "b500_pc_closed_forest_forest_total", "b500_pc_herbaceous_wetland", "b3km_pc_herbaceous_vegetation", "city_pc_cultivated", "city_pc_shrubs", "b500_pc_closed_forest_forest_other", "city_pc_urban", "region_pc_cultivated", "b1km_pc_permanent_water", "b5km_pc_bare", "region_pc_closed_forest_evergreen_needle", "elevation", "region_pc_closed_forest_forest_total", "region_pc_open_forest_evergreen_needle", "b5km_pc_closed_forest_evergreen_needle", "city_pc_closed_forest_evergreen_needle", "b500_pc_closed_forest_deciduous_broadleaf", "region_pc_permanent_water", "region_pc_open_forest_forest_other", "b500_pc_ocean", "city_pc_open_forest_forest_total", "city_pc_bare", "region_pc_bare", "city_pc_open_forest_forest_other", "city_pc_closed_forest_forest_total", "city_pc_closed_forest_forest_other", "region_pc_herbaceous_wetland", "region_pc_closed_forest_deciduous_broadleaf", "region_pc_urban", "city_pc_herbaceous_wetland", "pop_2015", "region_pc_closed_forest_forest_other", "city_pc_herbaceous_vegetation", "region_pc_closed_forest_evergreen_broadleaf", "region_pc_open_forest_deciduous_broadleaf", "city_pc_closed_forest_deciduous_broadleaf")])
create_fifty_rows_of_oob(data[,c("locality_project_richness", "b500_pc_urban", "b500_avg_pop_density", "b500_pc_open_forest_forest_other", "b500_pc_open_forest_forest_total", "region_pc_shrubs", "latitude", "number_of_checklists", "b1km_pc_shrubs", "b1km_pc_cultivated", "city_pc_permanent_water", "b500_pc_closed_forest_forest_total", "b500_pc_herbaceous_wetland", "b3km_pc_herbaceous_vegetation", "city_pc_cultivated", "city_pc_shrubs", "b500_pc_closed_forest_forest_other", "city_pc_urban", "region_pc_cultivated", "b1km_pc_permanent_water", "b5km_pc_bare", "region_pc_closed_forest_evergreen_needle", "elevation", "region_pc_closed_forest_forest_total", "region_pc_open_forest_evergreen_needle", "b5km_pc_closed_forest_evergreen_needle", "city_pc_closed_forest_evergreen_needle", "b500_pc_closed_forest_deciduous_broadleaf", "region_pc_permanent_water", "region_pc_open_forest_forest_other", "b500_pc_ocean", "city_pc_open_forest_forest_total", "city_pc_bare", "region_pc_bare", "city_pc_open_forest_forest_other", "city_pc_closed_forest_forest_total", "city_pc_closed_forest_forest_other", "region_pc_herbaceous_wetland", "region_pc_closed_forest_deciduous_broadleaf", "region_pc_urban", "city_pc_herbaceous_wetland", "pop_2015", "region_pc_closed_forest_forest_other", "city_pc_herbaceous_vegetation", "region_pc_closed_forest_evergreen_broadleaf", "region_pc_open_forest_deciduous_broadleaf", "city_pc_closed_forest_deciduous_broadleaf", "region_pc_closed_forest_forest_mixed")])
create_fifty_rows_of_oob(data[,c("locality_project_richness", "b500_pc_urban", "b500_avg_pop_density", "b500_pc_open_forest_forest_other", "b500_pc_open_forest_forest_total", "region_pc_shrubs", "latitude", "number_of_checklists", "b1km_pc_shrubs", "b1km_pc_cultivated", "city_pc_permanent_water", "b500_pc_closed_forest_forest_total", "b500_pc_herbaceous_wetland", "b3km_pc_herbaceous_vegetation", "city_pc_cultivated", "city_pc_shrubs", "b500_pc_closed_forest_forest_other", "city_pc_urban", "region_pc_cultivated", "b1km_pc_permanent_water", "b5km_pc_bare", "region_pc_closed_forest_evergreen_needle", "elevation", "region_pc_closed_forest_forest_total", "region_pc_open_forest_evergreen_needle", "b5km_pc_closed_forest_evergreen_needle", "city_pc_closed_forest_evergreen_needle", "b500_pc_closed_forest_deciduous_broadleaf", "region_pc_permanent_water", "region_pc_open_forest_forest_other", "b500_pc_ocean", "city_pc_open_forest_forest_total", "city_pc_bare", "region_pc_bare", "city_pc_open_forest_forest_other", "city_pc_closed_forest_forest_total", "city_pc_closed_forest_forest_other", "region_pc_herbaceous_wetland", "region_pc_closed_forest_deciduous_broadleaf", "region_pc_urban", "city_pc_herbaceous_wetland", "pop_2015", "region_pc_closed_forest_forest_other", "city_pc_herbaceous_vegetation", "region_pc_closed_forest_evergreen_broadleaf", "region_pc_open_forest_deciduous_broadleaf", "city_pc_closed_forest_deciduous_broadleaf", "region_pc_closed_forest_forest_mixed", "b5km_pc_open_forest_evergreen_needle")])
create_fifty_rows_of_oob(data[,c("locality_project_richness", "b500_pc_urban", "b500_avg_pop_density", "b500_pc_open_forest_forest_other", "b500_pc_open_forest_forest_total", "region_pc_shrubs", "latitude", "number_of_checklists", "b1km_pc_shrubs", "b1km_pc_cultivated", "city_pc_permanent_water", "b500_pc_closed_forest_forest_total", "b500_pc_herbaceous_wetland", "b3km_pc_herbaceous_vegetation", "city_pc_cultivated", "city_pc_shrubs", "b500_pc_closed_forest_forest_other", "city_pc_urban", "region_pc_cultivated", "b1km_pc_permanent_water", "b5km_pc_bare", "region_pc_closed_forest_evergreen_needle", "elevation", "region_pc_closed_forest_forest_total", "region_pc_open_forest_evergreen_needle", "b5km_pc_closed_forest_evergreen_needle", "city_pc_closed_forest_evergreen_needle", "b500_pc_closed_forest_deciduous_broadleaf", "region_pc_permanent_water", "region_pc_open_forest_forest_other", "b500_pc_ocean", "city_pc_open_forest_forest_total", "city_pc_bare", "region_pc_bare", "city_pc_open_forest_forest_other", "city_pc_closed_forest_forest_total", "city_pc_closed_forest_forest_other", "region_pc_herbaceous_wetland", "region_pc_closed_forest_deciduous_broadleaf", "region_pc_urban", "city_pc_herbaceous_wetland", "pop_2015", "region_pc_closed_forest_forest_other", "city_pc_herbaceous_vegetation", "region_pc_closed_forest_evergreen_broadleaf", "region_pc_open_forest_deciduous_broadleaf", "city_pc_closed_forest_deciduous_broadleaf", "region_pc_closed_forest_forest_mixed", "b5km_pc_open_forest_evergreen_needle", "region_pc_open_forest_evergreen_broadleaf")])
create_fifty_rows_of_oob(data[,c("locality_project_richness", "b500_pc_urban", "b500_avg_pop_density", "b500_pc_open_forest_forest_other", "b500_pc_open_forest_forest_total", "region_pc_shrubs", "latitude", "number_of_checklists", "b1km_pc_shrubs", "b1km_pc_cultivated", "city_pc_permanent_water", "b500_pc_closed_forest_forest_total", "b500_pc_herbaceous_wetland", "b3km_pc_herbaceous_vegetation", "city_pc_cultivated", "city_pc_shrubs", "b500_pc_closed_forest_forest_other", "city_pc_urban", "region_pc_cultivated", "b1km_pc_permanent_water", "b5km_pc_bare", "region_pc_closed_forest_evergreen_needle", "elevation", "region_pc_closed_forest_forest_total", "region_pc_open_forest_evergreen_needle", "b5km_pc_closed_forest_evergreen_needle", "city_pc_closed_forest_evergreen_needle", "b500_pc_closed_forest_deciduous_broadleaf", "region_pc_permanent_water", "region_pc_open_forest_forest_other", "b500_pc_ocean", "city_pc_open_forest_forest_total", "city_pc_bare", "region_pc_bare", "city_pc_open_forest_forest_other", "city_pc_closed_forest_forest_total", "city_pc_closed_forest_forest_other", "region_pc_herbaceous_wetland", "region_pc_closed_forest_deciduous_broadleaf", "region_pc_urban", "city_pc_herbaceous_wetland", "pop_2015", "region_pc_closed_forest_forest_other", "city_pc_herbaceous_vegetation", "region_pc_closed_forest_evergreen_broadleaf", "region_pc_open_forest_deciduous_broadleaf", "city_pc_closed_forest_deciduous_broadleaf", "region_pc_closed_forest_forest_mixed", "b5km_pc_open_forest_evergreen_needle", "region_pc_open_forest_evergreen_broadleaf", "region_pc_ocean")])
create_fifty_rows_of_oob(data[,c("locality_project_richness", "b500_pc_urban", "b500_avg_pop_density", "b500_pc_open_forest_forest_other", "b500_pc_open_forest_forest_total", "region_pc_shrubs", "latitude", "number_of_checklists", "b1km_pc_shrubs", "b1km_pc_cultivated", "city_pc_permanent_water", "b500_pc_closed_forest_forest_total", "b500_pc_herbaceous_wetland", "b3km_pc_herbaceous_vegetation", "city_pc_cultivated", "city_pc_shrubs", "b500_pc_closed_forest_forest_other", "city_pc_urban", "region_pc_cultivated", "b1km_pc_permanent_water", "b5km_pc_bare", "region_pc_closed_forest_evergreen_needle", "elevation", "region_pc_closed_forest_forest_total", "region_pc_open_forest_evergreen_needle", "b5km_pc_closed_forest_evergreen_needle", "city_pc_closed_forest_evergreen_needle", "b500_pc_closed_forest_deciduous_broadleaf", "region_pc_permanent_water", "region_pc_open_forest_forest_other", "b500_pc_ocean", "city_pc_open_forest_forest_total", "city_pc_bare", "region_pc_bare", "city_pc_open_forest_forest_other", "city_pc_closed_forest_forest_total", "city_pc_closed_forest_forest_other", "region_pc_herbaceous_wetland", "region_pc_closed_forest_deciduous_broadleaf", "region_pc_urban", "city_pc_herbaceous_wetland", "pop_2015", "region_pc_closed_forest_forest_other", "city_pc_herbaceous_vegetation", "region_pc_closed_forest_evergreen_broadleaf", "region_pc_open_forest_deciduous_broadleaf", "city_pc_closed_forest_deciduous_broadleaf", "region_pc_closed_forest_forest_mixed", "b5km_pc_open_forest_evergreen_needle", "region_pc_open_forest_evergreen_broadleaf", "region_pc_ocean", "city_pc_open_forest_deciduous_broadleaf")])
create_fifty_rows_of_oob(data[,c("locality_project_richness", "b500_pc_urban", "b500_avg_pop_density", "b500_pc_open_forest_forest_other", "b500_pc_open_forest_forest_total", "region_pc_shrubs", "latitude", "number_of_checklists", "b1km_pc_shrubs", "b1km_pc_cultivated", "city_pc_permanent_water", "b500_pc_closed_forest_forest_total", "b500_pc_herbaceous_wetland", "b3km_pc_herbaceous_vegetation", "city_pc_cultivated", "city_pc_shrubs", "b500_pc_closed_forest_forest_other", "city_pc_urban", "region_pc_cultivated", "b1km_pc_permanent_water", "b5km_pc_bare", "region_pc_closed_forest_evergreen_needle", "elevation", "region_pc_closed_forest_forest_total", "region_pc_open_forest_evergreen_needle", "b5km_pc_closed_forest_evergreen_needle", "city_pc_closed_forest_evergreen_needle", "b500_pc_closed_forest_deciduous_broadleaf", "region_pc_permanent_water", "region_pc_open_forest_forest_other", "b500_pc_ocean", "city_pc_open_forest_forest_total", "city_pc_bare", "region_pc_bare", "city_pc_open_forest_forest_other", "city_pc_closed_forest_forest_total", "city_pc_closed_forest_forest_other", "region_pc_herbaceous_wetland", "region_pc_closed_forest_deciduous_broadleaf", "region_pc_urban", "city_pc_herbaceous_wetland", "pop_2015", "region_pc_closed_forest_forest_other", "city_pc_herbaceous_vegetation", "region_pc_closed_forest_evergreen_broadleaf", "region_pc_open_forest_deciduous_broadleaf", "city_pc_closed_forest_deciduous_broadleaf", "region_pc_closed_forest_forest_mixed", "b5km_pc_open_forest_evergreen_needle", "region_pc_open_forest_evergreen_broadleaf", "region_pc_ocean", "city_pc_open_forest_deciduous_broadleaf", "b5km_pc_closed_forest_forest_mixed")])
create_fifty_rows_of_oob(data[,c("locality_project_richness", "b500_pc_urban", "b500_avg_pop_density", "b500_pc_open_forest_forest_other", "b500_pc_open_forest_forest_total", "region_pc_shrubs", "latitude", "number_of_checklists", "b1km_pc_shrubs", "b1km_pc_cultivated", "city_pc_permanent_water", "b500_pc_closed_forest_forest_total", "b500_pc_herbaceous_wetland", "b3km_pc_herbaceous_vegetation", "city_pc_cultivated", "city_pc_shrubs", "b500_pc_closed_forest_forest_other", "city_pc_urban", "region_pc_cultivated", "b1km_pc_permanent_water", "b5km_pc_bare", "region_pc_closed_forest_evergreen_needle", "elevation", "region_pc_closed_forest_forest_total", "region_pc_open_forest_evergreen_needle", "b5km_pc_closed_forest_evergreen_needle", "city_pc_closed_forest_evergreen_needle", "b500_pc_closed_forest_deciduous_broadleaf", "region_pc_permanent_water", "region_pc_open_forest_forest_other", "b500_pc_ocean", "city_pc_open_forest_forest_total", "city_pc_bare", "region_pc_bare", "city_pc_open_forest_forest_other", "city_pc_closed_forest_forest_total", "city_pc_closed_forest_forest_other", "region_pc_herbaceous_wetland", "region_pc_closed_forest_deciduous_broadleaf", "region_pc_urban", "city_pc_herbaceous_wetland", "pop_2015", "region_pc_closed_forest_forest_other", "city_pc_herbaceous_vegetation", "region_pc_closed_forest_evergreen_broadleaf", "region_pc_open_forest_deciduous_broadleaf", "city_pc_closed_forest_deciduous_broadleaf", "region_pc_closed_forest_forest_mixed", "b5km_pc_open_forest_evergreen_needle", "region_pc_open_forest_evergreen_broadleaf", "region_pc_ocean", "city_pc_open_forest_deciduous_broadleaf", "b5km_pc_closed_forest_forest_mixed", "region_pc_open_forest_forest_mixed")])
create_fifty_rows_of_oob(data[,c("locality_project_richness", "b500_pc_urban", "b500_avg_pop_density", "b500_pc_open_forest_forest_other", "b500_pc_open_forest_forest_total", "region_pc_shrubs", "latitude", "number_of_checklists", "b1km_pc_shrubs", "b1km_pc_cultivated", "city_pc_permanent_water", "b500_pc_closed_forest_forest_total", "b500_pc_herbaceous_wetland", "b3km_pc_herbaceous_vegetation", "city_pc_cultivated", "city_pc_shrubs", "b500_pc_closed_forest_forest_other", "city_pc_urban", "region_pc_cultivated", "b1km_pc_permanent_water", "b5km_pc_bare", "region_pc_closed_forest_evergreen_needle", "elevation", "region_pc_closed_forest_forest_total", "region_pc_open_forest_evergreen_needle", "b5km_pc_closed_forest_evergreen_needle", "city_pc_closed_forest_evergreen_needle", "b500_pc_closed_forest_deciduous_broadleaf", "region_pc_permanent_water", "region_pc_open_forest_forest_other", "b500_pc_ocean", "city_pc_open_forest_forest_total", "city_pc_bare", "region_pc_bare", "city_pc_open_forest_forest_other", "city_pc_closed_forest_forest_total", "city_pc_closed_forest_forest_other", "region_pc_herbaceous_wetland", "region_pc_closed_forest_deciduous_broadleaf", "region_pc_urban", "city_pc_herbaceous_wetland", "pop_2015", "region_pc_closed_forest_forest_other", "city_pc_herbaceous_vegetation", "region_pc_closed_forest_evergreen_broadleaf", "region_pc_open_forest_deciduous_broadleaf", "city_pc_closed_forest_deciduous_broadleaf", "region_pc_closed_forest_forest_mixed", "b5km_pc_open_forest_evergreen_needle", "region_pc_open_forest_evergreen_broadleaf", "region_pc_ocean", "city_pc_open_forest_deciduous_broadleaf", "b5km_pc_closed_forest_forest_mixed", "region_pc_open_forest_forest_mixed", "city_pc_closed_forest_forest_mixed")])
create_fifty_rows_of_oob(data[,c("locality_project_richness", "b500_pc_urban", "b500_avg_pop_density", "b500_pc_open_forest_forest_other", "b500_pc_open_forest_forest_total", "region_pc_shrubs", "latitude", "number_of_checklists", "b1km_pc_shrubs", "b1km_pc_cultivated", "city_pc_permanent_water", "b500_pc_closed_forest_forest_total", "b500_pc_herbaceous_wetland", "b3km_pc_herbaceous_vegetation", "city_pc_cultivated", "city_pc_shrubs", "b500_pc_closed_forest_forest_other", "city_pc_urban", "region_pc_cultivated", "b1km_pc_permanent_water", "b5km_pc_bare", "region_pc_closed_forest_evergreen_needle", "elevation", "region_pc_closed_forest_forest_total", "region_pc_open_forest_evergreen_needle", "b5km_pc_closed_forest_evergreen_needle", "city_pc_closed_forest_evergreen_needle", "b500_pc_closed_forest_deciduous_broadleaf", "region_pc_permanent_water", "region_pc_open_forest_forest_other", "b500_pc_ocean", "city_pc_open_forest_forest_total", "city_pc_bare", "region_pc_bare", "city_pc_open_forest_forest_other", "city_pc_closed_forest_forest_total", "city_pc_closed_forest_forest_other", "region_pc_herbaceous_wetland", "region_pc_closed_forest_deciduous_broadleaf", "region_pc_urban", "city_pc_herbaceous_wetland", "pop_2015", "region_pc_closed_forest_forest_other", "city_pc_herbaceous_vegetation", "region_pc_closed_forest_evergreen_broadleaf", "region_pc_open_forest_deciduous_broadleaf", "city_pc_closed_forest_deciduous_broadleaf", "region_pc_closed_forest_forest_mixed", "b5km_pc_open_forest_evergreen_needle", "region_pc_open_forest_evergreen_broadleaf", "region_pc_ocean", "city_pc_open_forest_deciduous_broadleaf", "b5km_pc_closed_forest_forest_mixed", "region_pc_open_forest_forest_mixed", "city_pc_closed_forest_forest_mixed", "city_pc_ocean")])
create_fifty_rows_of_oob(data[,c("locality_project_richness", "b500_pc_urban", "b500_avg_pop_density", "b500_pc_open_forest_forest_other", "b500_pc_open_forest_forest_total", "region_pc_shrubs", "latitude", "number_of_checklists", "b1km_pc_shrubs", "b1km_pc_cultivated", "city_pc_permanent_water", "b500_pc_closed_forest_forest_total", "b500_pc_herbaceous_wetland", "b3km_pc_herbaceous_vegetation", "city_pc_cultivated", "city_pc_shrubs", "b500_pc_closed_forest_forest_other", "city_pc_urban", "region_pc_cultivated", "b1km_pc_permanent_water", "b5km_pc_bare", "region_pc_closed_forest_evergreen_needle", "elevation", "region_pc_closed_forest_forest_total", "region_pc_open_forest_evergreen_needle", "b5km_pc_closed_forest_evergreen_needle", "city_pc_closed_forest_evergreen_needle", "b500_pc_closed_forest_deciduous_broadleaf", "region_pc_permanent_water", "region_pc_open_forest_forest_other", "b500_pc_ocean", "city_pc_open_forest_forest_total", "city_pc_bare", "region_pc_bare", "city_pc_open_forest_forest_other", "city_pc_closed_forest_forest_total", "city_pc_closed_forest_forest_other", "region_pc_herbaceous_wetland", "region_pc_closed_forest_deciduous_broadleaf", "region_pc_urban", "city_pc_herbaceous_wetland", "pop_2015", "region_pc_closed_forest_forest_other", "city_pc_herbaceous_vegetation", "region_pc_closed_forest_evergreen_broadleaf", "region_pc_open_forest_deciduous_broadleaf", "city_pc_closed_forest_deciduous_broadleaf", "region_pc_closed_forest_forest_mixed", "b5km_pc_open_forest_evergreen_needle", "region_pc_open_forest_evergreen_broadleaf", "region_pc_ocean", "city_pc_open_forest_deciduous_broadleaf", "b5km_pc_closed_forest_forest_mixed", "region_pc_open_forest_forest_mixed", "city_pc_closed_forest_forest_mixed", "city_pc_ocean", "b5km_pc_closed_forest_evergreen_broadleaf")])
create_fifty_rows_of_oob(data[,c("locality_project_richness", "b500_pc_urban", "b500_avg_pop_density", "b500_pc_open_forest_forest_other", "b500_pc_open_forest_forest_total", "region_pc_shrubs", "latitude", "number_of_checklists", "b1km_pc_shrubs", "b1km_pc_cultivated", "city_pc_permanent_water", "b500_pc_closed_forest_forest_total", "b500_pc_herbaceous_wetland", "b3km_pc_herbaceous_vegetation", "city_pc_cultivated", "city_pc_shrubs", "b500_pc_closed_forest_forest_other", "city_pc_urban", "region_pc_cultivated", "b1km_pc_permanent_water", "b5km_pc_bare", "region_pc_closed_forest_evergreen_needle", "elevation", "region_pc_closed_forest_forest_total", "region_pc_open_forest_evergreen_needle", "b5km_pc_closed_forest_evergreen_needle", "city_pc_closed_forest_evergreen_needle", "b500_pc_closed_forest_deciduous_broadleaf", "region_pc_permanent_water", "region_pc_open_forest_forest_other", "b500_pc_ocean", "city_pc_open_forest_forest_total", "city_pc_bare", "region_pc_bare", "city_pc_open_forest_forest_other", "city_pc_closed_forest_forest_total", "city_pc_closed_forest_forest_other", "region_pc_herbaceous_wetland", "region_pc_closed_forest_deciduous_broadleaf", "region_pc_urban", "city_pc_herbaceous_wetland", "pop_2015", "region_pc_closed_forest_forest_other", "city_pc_herbaceous_vegetation", "region_pc_closed_forest_evergreen_broadleaf", "region_pc_open_forest_deciduous_broadleaf", "city_pc_closed_forest_deciduous_broadleaf", "region_pc_closed_forest_forest_mixed", "b5km_pc_open_forest_evergreen_needle", "region_pc_open_forest_evergreen_broadleaf", "region_pc_ocean", "city_pc_open_forest_deciduous_broadleaf", "b5km_pc_closed_forest_forest_mixed", "region_pc_open_forest_forest_mixed", "city_pc_closed_forest_forest_mixed", "city_pc_ocean", "b5km_pc_closed_forest_evergreen_broadleaf", "region_pc_snow")])
create_fifty_rows_of_oob(data[,c("locality_project_richness", "b500_pc_urban", "b500_avg_pop_density", "b500_pc_open_forest_forest_other", "b500_pc_open_forest_forest_total", "region_pc_shrubs", "latitude", "number_of_checklists", "b1km_pc_shrubs", "b1km_pc_cultivated", "city_pc_permanent_water", "b500_pc_closed_forest_forest_total", "b500_pc_herbaceous_wetland", "b3km_pc_herbaceous_vegetation", "city_pc_cultivated", "city_pc_shrubs", "b500_pc_closed_forest_forest_other", "city_pc_urban", "region_pc_cultivated", "b1km_pc_permanent_water", "b5km_pc_bare", "region_pc_closed_forest_evergreen_needle", "elevation", "region_pc_closed_forest_forest_total", "region_pc_open_forest_evergreen_needle", "b5km_pc_closed_forest_evergreen_needle", "city_pc_closed_forest_evergreen_needle", "b500_pc_closed_forest_deciduous_broadleaf", "region_pc_permanent_water", "region_pc_open_forest_forest_other", "b500_pc_ocean", "city_pc_open_forest_forest_total", "city_pc_bare", "region_pc_bare", "city_pc_open_forest_forest_other", "city_pc_closed_forest_forest_total", "city_pc_closed_forest_forest_other", "region_pc_herbaceous_wetland", "region_pc_closed_forest_deciduous_broadleaf", "region_pc_urban", "city_pc_herbaceous_wetland", "pop_2015", "region_pc_closed_forest_forest_other", "city_pc_herbaceous_vegetation", "region_pc_closed_forest_evergreen_broadleaf", "region_pc_open_forest_deciduous_broadleaf", "city_pc_closed_forest_deciduous_broadleaf", "region_pc_closed_forest_forest_mixed", "b5km_pc_open_forest_evergreen_needle", "region_pc_open_forest_evergreen_broadleaf", "region_pc_ocean", "city_pc_open_forest_deciduous_broadleaf", "b5km_pc_closed_forest_forest_mixed", "region_pc_open_forest_forest_mixed", "city_pc_closed_forest_forest_mixed", "city_pc_ocean", "b5km_pc_closed_forest_evergreen_broadleaf", "region_pc_snow", "b5km_pc_open_forest_deciduous_broadleaf")])
create_fifty_rows_of_oob(data[,c("locality_project_richness", "b500_pc_urban", "b500_avg_pop_density", "b500_pc_open_forest_forest_other", "b500_pc_open_forest_forest_total", "region_pc_shrubs", "latitude", "number_of_checklists", "b1km_pc_shrubs", "b1km_pc_cultivated", "city_pc_permanent_water", "b500_pc_closed_forest_forest_total", "b500_pc_herbaceous_wetland", "b3km_pc_herbaceous_vegetation", "city_pc_cultivated", "city_pc_shrubs", "b500_pc_closed_forest_forest_other", "city_pc_urban", "region_pc_cultivated", "b1km_pc_permanent_water", "b5km_pc_bare", "region_pc_closed_forest_evergreen_needle", "elevation", "region_pc_closed_forest_forest_total", "region_pc_open_forest_evergreen_needle", "b5km_pc_closed_forest_evergreen_needle", "city_pc_closed_forest_evergreen_needle", "b500_pc_closed_forest_deciduous_broadleaf", "region_pc_permanent_water", "region_pc_open_forest_forest_other", "b500_pc_ocean", "city_pc_open_forest_forest_total", "city_pc_bare", "region_pc_bare", "city_pc_open_forest_forest_other", "city_pc_closed_forest_forest_total", "city_pc_closed_forest_forest_other", "region_pc_herbaceous_wetland", "region_pc_closed_forest_deciduous_broadleaf", "region_pc_urban", "city_pc_herbaceous_wetland", "pop_2015", "region_pc_closed_forest_forest_other", "city_pc_herbaceous_vegetation", "region_pc_closed_forest_evergreen_broadleaf", "region_pc_open_forest_deciduous_broadleaf", "city_pc_closed_forest_deciduous_broadleaf", "region_pc_closed_forest_forest_mixed", "b5km_pc_open_forest_evergreen_needle", "region_pc_open_forest_evergreen_broadleaf", "region_pc_ocean", "city_pc_open_forest_deciduous_broadleaf", "b5km_pc_closed_forest_forest_mixed", "region_pc_open_forest_forest_mixed", "city_pc_closed_forest_forest_mixed", "city_pc_ocean", "b5km_pc_closed_forest_evergreen_broadleaf", "region_pc_snow", "b5km_pc_open_forest_deciduous_broadleaf", "city_pc_open_forest_evergreen_broadleaf")])
create_fifty_rows_of_oob(data[,c("locality_project_richness", "b500_pc_urban", "b500_avg_pop_density", "b500_pc_open_forest_forest_other", "b500_pc_open_forest_forest_total", "region_pc_shrubs", "latitude", "number_of_checklists", "b1km_pc_shrubs", "b1km_pc_cultivated", "city_pc_permanent_water", "b500_pc_closed_forest_forest_total", "b500_pc_herbaceous_wetland", "b3km_pc_herbaceous_vegetation", "city_pc_cultivated", "city_pc_shrubs", "b500_pc_closed_forest_forest_other", "city_pc_urban", "region_pc_cultivated", "b1km_pc_permanent_water", "b5km_pc_bare", "region_pc_closed_forest_evergreen_needle", "elevation", "region_pc_closed_forest_forest_total", "region_pc_open_forest_evergreen_needle", "b5km_pc_closed_forest_evergreen_needle", "city_pc_closed_forest_evergreen_needle", "b500_pc_closed_forest_deciduous_broadleaf", "region_pc_permanent_water", "region_pc_open_forest_forest_other", "b500_pc_ocean", "city_pc_open_forest_forest_total", "city_pc_bare", "region_pc_bare", "city_pc_open_forest_forest_other", "city_pc_closed_forest_forest_total", "city_pc_closed_forest_forest_other", "region_pc_herbaceous_wetland", "region_pc_closed_forest_deciduous_broadleaf", "region_pc_urban", "city_pc_herbaceous_wetland", "pop_2015", "region_pc_closed_forest_forest_other", "city_pc_herbaceous_vegetation", "region_pc_closed_forest_evergreen_broadleaf", "region_pc_open_forest_deciduous_broadleaf", "city_pc_closed_forest_deciduous_broadleaf", "region_pc_closed_forest_forest_mixed", "b5km_pc_open_forest_evergreen_needle", "region_pc_open_forest_evergreen_broadleaf", "region_pc_ocean", "city_pc_open_forest_deciduous_broadleaf", "b5km_pc_closed_forest_forest_mixed", "region_pc_open_forest_forest_mixed", "city_pc_closed_forest_forest_mixed", "city_pc_ocean", "b5km_pc_closed_forest_evergreen_broadleaf", "region_pc_snow", "b5km_pc_open_forest_deciduous_broadleaf", "city_pc_open_forest_evergreen_broadleaf", "city_pc_open_forest_evergreen_needle")])
create_fifty_rows_of_oob(data[,c("locality_project_richness", "b500_pc_urban", "b500_avg_pop_density", "b500_pc_open_forest_forest_other", "b500_pc_open_forest_forest_total", "region_pc_shrubs", "latitude", "number_of_checklists", "b1km_pc_shrubs", "b1km_pc_cultivated", "city_pc_permanent_water", "b500_pc_closed_forest_forest_total", "b500_pc_herbaceous_wetland", "b3km_pc_herbaceous_vegetation", "city_pc_cultivated", "city_pc_shrubs", "b500_pc_closed_forest_forest_other", "city_pc_urban", "region_pc_cultivated", "b1km_pc_permanent_water", "b5km_pc_bare", "region_pc_closed_forest_evergreen_needle", "elevation", "region_pc_closed_forest_forest_total", "region_pc_open_forest_evergreen_needle", "b5km_pc_closed_forest_evergreen_needle", "city_pc_closed_forest_evergreen_needle", "b500_pc_closed_forest_deciduous_broadleaf", "region_pc_permanent_water", "region_pc_open_forest_forest_other", "b500_pc_ocean", "city_pc_open_forest_forest_total", "city_pc_bare", "region_pc_bare", "city_pc_open_forest_forest_other", "city_pc_closed_forest_forest_total", "city_pc_closed_forest_forest_other", "region_pc_herbaceous_wetland", "region_pc_closed_forest_deciduous_broadleaf", "region_pc_urban", "city_pc_herbaceous_wetland", "pop_2015", "region_pc_closed_forest_forest_other", "city_pc_herbaceous_vegetation", "region_pc_closed_forest_evergreen_broadleaf", "region_pc_open_forest_deciduous_broadleaf", "city_pc_closed_forest_deciduous_broadleaf", "region_pc_closed_forest_forest_mixed", "b5km_pc_open_forest_evergreen_needle", "region_pc_open_forest_evergreen_broadleaf", "region_pc_ocean", "city_pc_open_forest_deciduous_broadleaf", "b5km_pc_closed_forest_forest_mixed", "region_pc_open_forest_forest_mixed", "city_pc_closed_forest_forest_mixed", "city_pc_ocean", "b5km_pc_closed_forest_evergreen_broadleaf", "region_pc_snow", "b5km_pc_open_forest_deciduous_broadleaf", "city_pc_open_forest_evergreen_broadleaf", "city_pc_open_forest_evergreen_needle", "b5km_pc_open_forest_evergreen_broadleaf")])
create_fifty_rows_of_oob(data[,c("locality_project_richness", "b500_pc_urban", "b500_avg_pop_density", "b500_pc_open_forest_forest_other", "b500_pc_open_forest_forest_total", "region_pc_shrubs", "latitude", "number_of_checklists", "b1km_pc_shrubs", "b1km_pc_cultivated", "city_pc_permanent_water", "b500_pc_closed_forest_forest_total", "b500_pc_herbaceous_wetland", "b3km_pc_herbaceous_vegetation", "city_pc_cultivated", "city_pc_shrubs", "b500_pc_closed_forest_forest_other", "city_pc_urban", "region_pc_cultivated", "b1km_pc_permanent_water", "b5km_pc_bare", "region_pc_closed_forest_evergreen_needle", "elevation", "region_pc_closed_forest_forest_total", "region_pc_open_forest_evergreen_needle", "b5km_pc_closed_forest_evergreen_needle", "city_pc_closed_forest_evergreen_needle", "b500_pc_closed_forest_deciduous_broadleaf", "region_pc_permanent_water", "region_pc_open_forest_forest_other", "b500_pc_ocean", "city_pc_open_forest_forest_total", "city_pc_bare", "region_pc_bare", "city_pc_open_forest_forest_other", "city_pc_closed_forest_forest_total", "city_pc_closed_forest_forest_other", "region_pc_herbaceous_wetland", "region_pc_closed_forest_deciduous_broadleaf", "region_pc_urban", "city_pc_herbaceous_wetland", "pop_2015", "region_pc_closed_forest_forest_other", "city_pc_herbaceous_vegetation", "region_pc_closed_forest_evergreen_broadleaf", "region_pc_open_forest_deciduous_broadleaf", "city_pc_closed_forest_deciduous_broadleaf", "region_pc_closed_forest_forest_mixed", "b5km_pc_open_forest_evergreen_needle", "region_pc_open_forest_evergreen_broadleaf", "region_pc_ocean", "city_pc_open_forest_deciduous_broadleaf", "b5km_pc_closed_forest_forest_mixed", "region_pc_open_forest_forest_mixed", "city_pc_closed_forest_forest_mixed", "city_pc_ocean", "b5km_pc_closed_forest_evergreen_broadleaf", "region_pc_snow", "b5km_pc_open_forest_deciduous_broadleaf", "city_pc_open_forest_evergreen_broadleaf", "city_pc_open_forest_evergreen_needle", "b5km_pc_open_forest_evergreen_broadleaf", "city_pc_closed_forest_evergreen_broadleaf")])
create_fifty_rows_of_oob(data[,c("locality_project_richness", "b500_pc_urban", "b500_avg_pop_density", "b500_pc_open_forest_forest_other", "b500_pc_open_forest_forest_total", "region_pc_shrubs", "latitude", "number_of_checklists", "b1km_pc_shrubs", "b1km_pc_cultivated", "city_pc_permanent_water", "b500_pc_closed_forest_forest_total", "b500_pc_herbaceous_wetland", "b3km_pc_herbaceous_vegetation", "city_pc_cultivated", "city_pc_shrubs", "b500_pc_closed_forest_forest_other", "city_pc_urban", "region_pc_cultivated", "b1km_pc_permanent_water", "b5km_pc_bare", "region_pc_closed_forest_evergreen_needle", "elevation", "region_pc_closed_forest_forest_total", "region_pc_open_forest_evergreen_needle", "b5km_pc_closed_forest_evergreen_needle", "city_pc_closed_forest_evergreen_needle", "b500_pc_closed_forest_deciduous_broadleaf", "region_pc_permanent_water", "region_pc_open_forest_forest_other", "b500_pc_ocean", "city_pc_open_forest_forest_total", "city_pc_bare", "region_pc_bare", "city_pc_open_forest_forest_other", "city_pc_closed_forest_forest_total", "city_pc_closed_forest_forest_other", "region_pc_herbaceous_wetland", "region_pc_closed_forest_deciduous_broadleaf", "region_pc_urban", "city_pc_herbaceous_wetland", "pop_2015", "region_pc_closed_forest_forest_other", "city_pc_herbaceous_vegetation", "region_pc_closed_forest_evergreen_broadleaf", "region_pc_open_forest_deciduous_broadleaf", "city_pc_closed_forest_deciduous_broadleaf", "region_pc_closed_forest_forest_mixed", "b5km_pc_open_forest_evergreen_needle", "region_pc_open_forest_evergreen_broadleaf", "region_pc_ocean", "city_pc_open_forest_deciduous_broadleaf", "b5km_pc_closed_forest_forest_mixed", "region_pc_open_forest_forest_mixed", "city_pc_closed_forest_forest_mixed", "city_pc_ocean", "b5km_pc_closed_forest_evergreen_broadleaf", "region_pc_snow", "b5km_pc_open_forest_deciduous_broadleaf", "city_pc_open_forest_evergreen_broadleaf", "city_pc_open_forest_evergreen_needle", "b5km_pc_open_forest_evergreen_broadleaf", "city_pc_closed_forest_evergreen_broadleaf", "region_pc_unknown")])

```
[1] 237.0585545   0.4036481 237.4622026
[1] 218.1458812   0.3908493 218.5367305
[1] 215.6906060   0.4501034 216.1407094
[1] 187.4073695   0.3982198 187.8055892
[1] 174.3622497   0.4933562 174.8556059
[1] 164.655811   0.370785 165.026596
[1] 164.3013576   0.4185055 164.7198631
[1] 159.4549015   0.3888992 159.8438007
[1] 156.7477219   0.3463417 157.0940636
[1] 152.6768138   0.3933915 153.0702053
[1] 149.2953546   0.3477907 149.6431452
[1] 146.7227400   0.4023227 147.1250627
[1] 145.4472967   0.3833911 145.8306878
[1] 145.3455562   0.3458964 145.6914527
[1] 144.9421186   0.4236683 145.3657870
[1] 144.3817882   0.3899382 144.7717264
[1] 144.1143999   0.3362032 144.4506030
[1] 142.7063116   0.3346706 143.0409821
[1] 141.9666000   0.3522233 142.3188233
[1] 141.7653731   0.3070641 142.0724373
[1] 140.9631356   0.3725054 141.3356410
[1] 140.8841132   0.3543562 141.2384694
[1] 140.7499803   0.3999639 141.1499442
[1] 140.0837193   0.3600603 140.4437796
[1] 139.9770030   0.4299025 140.4069055
[1] 139.7054772   0.3415725 140.0470497
[1] 139.4950209   0.4339608 139.9289817
[1] 139.2367927   0.3517541 139.5885469
[1] 138.8937076   0.3877111 139.2814187
[1] 138.7225731   0.3463675 139.0689406
[1] 138.6250656   0.3780332 139.0030988
[1] 138.6776775   0.3756454 139.0533229
[1] 138.5791399   0.3543379 138.9334778
[1] 138.4959956   0.3750295 138.8710251
[1] 138.639223   0.326065 138.965288
[1] 138.5073939   0.3448314 138.8522253
[1] 138.3947969   0.3919446 138.7867415
[1] 138.5162478   0.3174409 138.8336887
[1] 138.414962   0.378825 138.793787
[1] 138.3266329   0.3123088 138.6389417
[1] 138.4877325   0.4134386 138.9011711
[1] 138.3125202   0.4000265 138.7125467
[1] 138.2442249   0.3692172 138.6134421
[1] 138.3653174   0.3709456 138.7362629
[1] 138.3451530   0.3664333 138.7115863
[1] 138.2880550   0.3226711 138.6107261
[1] 138.3431109   0.3443736 138.6874846
[1] 138.2086366   0.3673946 138.5760312
[1] 138.141095   0.366729 138.507824
[1] 138.1914020   0.4028483 138.5942504
[1] 137.9775509   0.2982063 138.2757571
[1] 137.9943154   0.3294962 138.3238116
[1] 137.9968731   0.3703626 138.3672357
[1] 138.0947548   0.4354293 138.5301841
[1] 137.823234   0.393275 138.216509
[1] 138.0144048   0.3999737 138.4143785 <- chosen model
[1] 137.8488514   0.3605848 138.2094361
[1] 137.6818089   0.3687205 138.0505294 <- lowest score
[1] 137.7248427   0.3723474 138.0971901
[1] 137.7560753   0.4482137 138.2042890
[1] 137.7884546   0.3596147 138.1480693
[1] 137.7575813   0.3865365 138.1441179


create_fifty_rows_of_oob(data[,c("locality_project_richness", "b500_pc_urban", "b500_avg_pop_density", "b500_pc_open_forest_forest_other", "b500_pc_open_forest_forest_total", "region_pc_shrubs", "latitude", "number_of_checklists", "b1km_pc_shrubs", "b1km_pc_cultivated", "city_pc_permanent_water", "b500_pc_closed_forest_forest_total", "b500_pc_herbaceous_wetland", "b3km_pc_herbaceous_vegetation", "city_pc_cultivated", "city_pc_shrubs", "b500_pc_closed_forest_forest_other", "city_pc_urban", "region_pc_cultivated", "b1km_pc_permanent_water", "b5km_pc_bare", "region_pc_closed_forest_evergreen_needle", "elevation", "region_pc_closed_forest_forest_total", "region_pc_open_forest_evergreen_needle", "b5km_pc_closed_forest_evergreen_needle", "city_pc_closed_forest_evergreen_needle", "b500_pc_closed_forest_deciduous_broadleaf", "region_pc_permanent_water", "region_pc_open_forest_forest_other", "b500_pc_ocean", "city_pc_open_forest_forest_total", "city_pc_bare", "region_pc_bare", "city_pc_open_forest_forest_other", "city_pc_closed_forest_forest_total", "city_pc_closed_forest_forest_other", "region_pc_herbaceous_wetland", "region_pc_closed_forest_deciduous_broadleaf", "region_pc_urban", "city_pc_herbaceous_wetland", "pop_2015", "region_pc_closed_forest_forest_other", "city_pc_herbaceous_vegetation", "region_pc_closed_forest_evergreen_broadleaf", "region_pc_open_forest_deciduous_broadleaf", "city_pc_closed_forest_deciduous_broadleaf", "region_pc_closed_forest_forest_mixed", "b5km_pc_open_forest_evergreen_needle", "region_pc_open_forest_evergreen_broadleaf", "region_pc_ocean", "city_pc_open_forest_deciduous_broadleaf", "b5km_pc_closed_forest_forest_mixed", "region_pc_open_forest_forest_mixed", "city_pc_closed_forest_forest_mixed", "city_pc_ocean", "b5km_pc_closed_forest_evergreen_broadleaf", "region_pc_snow")])

latitude
number_of_checklists
elevation

b500_pc_urban
b500_avg_pop_density
b500_pc_open_forest_forest_other
b500_pc_open_forest_forest_total
b1km_pc_shrubs
b1km_pc_cultivated
b500_pc_closed_forest_forest_total
b500_pc_herbaceous_wetland
b3km_pc_herbaceous_vegetation
b500_pc_closed_forest_forest_other
b1km_pc_permanent_water
b5km_pc_bare
b5km_pc_closed_forest_evergreen_needle
b500_pc_ocean
b5km_pc_open_forest_evergreen_needle
b5km_pc_closed_forest_forest_mixed
b5km_pc_closed_forest_evergreen_broadleaf

city_pc_permanent_water
city_pc_cultivated
city_pc_shrubs
city_pc_urban
city_pc_closed_forest_evergreen_needle
city_pc_open_forest_forest_total
city_pc_bare
city_pc_open_forest_forest_other
city_pc_closed_forest_forest_total
city_pc_closed_forest_forest_other
city_pc_herbaceous_vegetation
city_pc_closed_forest_deciduous_broadleaf
city_pc_open_forest_deciduous_broadleaf
city_pc_closed_forest_forest_mixed
city_pc_ocean

region_pc_shrubs
region_pc_cultivated
region_pc_closed_forest_evergreen_needle
region_pc_closed_forest_forest_total
region_pc_open_forest_evergreen_needle
region_pc_bare
region_pc_herbaceous_wetland
region_pc_closed_forest_forest_other
region_pc_closed_forest_evergreen_broadleaf
region_pc_open_forest_deciduous_broadleaf
region_pc_closed_forest_forest_mixed
region_pc_open_forest_evergreen_broadleaf
region_pc_ocean
region_pc_open_forest_forest_mixed
region_pc_snow


Chosen Model (locality_richness)
------------

```{r}
data_choice <- data[c("locality_project_richness", "b500_pc_urban", "b500_avg_pop_density", "b500_pc_open_forest_forest_other", "b500_pc_open_forest_forest_total", "region_pc_shrubs", "latitude", "number_of_checklists", "b1km_pc_shrubs", "b1km_pc_cultivated", "city_pc_permanent_water", "b500_pc_closed_forest_forest_total", "b500_pc_herbaceous_wetland", "b3km_pc_herbaceous_vegetation", "city_pc_cultivated", "city_pc_shrubs", "b500_pc_closed_forest_forest_other", "city_pc_urban", "region_pc_cultivated", "b1km_pc_permanent_water", "b5km_pc_bare", "region_pc_closed_forest_evergreen_needle", "elevation", "region_pc_closed_forest_forest_total", "region_pc_open_forest_evergreen_needle", "b5km_pc_closed_forest_evergreen_needle", "city_pc_closed_forest_evergreen_needle", "b500_pc_closed_forest_deciduous_broadleaf", "region_pc_permanent_water", "region_pc_open_forest_forest_other", "b500_pc_ocean", "city_pc_open_forest_forest_total", "city_pc_bare", "region_pc_bare", "city_pc_open_forest_forest_other", "city_pc_closed_forest_forest_total", "city_pc_closed_forest_forest_other", "region_pc_herbaceous_wetland", "region_pc_closed_forest_deciduous_broadleaf", "region_pc_urban", "city_pc_herbaceous_wetland", "pop_2015", "region_pc_closed_forest_forest_other", "city_pc_herbaceous_vegetation", "region_pc_closed_forest_evergreen_broadleaf", "region_pc_open_forest_deciduous_broadleaf", "city_pc_closed_forest_deciduous_broadleaf", "region_pc_closed_forest_forest_mixed", "b5km_pc_open_forest_evergreen_needle", "region_pc_open_forest_evergreen_broadleaf", "region_pc_ocean", "city_pc_open_forest_deciduous_broadleaf", "b5km_pc_closed_forest_forest_mixed", "region_pc_open_forest_forest_mixed", "city_pc_closed_forest_forest_mixed", "city_pc_ocean", "b5km_pc_closed_forest_evergreen_broadleaf", "region_pc_snow")]


jpeg(filename = "pairs.jpg", width = 4048, height = 4048)
pairs(data_choice)
dev.off()

library(psych)
jpeg(filename = "pairs2.jpg", width = 4048, height = 4048)
pairs.panels(data_choice, 
 method = "pearson", # correlation method
 hist.col = "#00AFBB",
 density = TRUE,  # show density plots
 ellipses = TRUE # show correlation ellipses
 )
dev.off()
``` 




```{r}
model_gam <- gam(locality_project_richness ~ s(b500_pc_urban) + s(b500_avg_pop_density) + s(b500_pc_open_forest_forest_other) + s(b500_pc_open_forest_forest_total) + s(region_pc_shrubs) + s(latitude) + s(number_of_checklists) + s(b1km_pc_shrubs) + s(b1km_pc_cultivated) + s(city_pc_permanent_water) + s(b500_pc_closed_forest_forest_total) + s(b500_pc_herbaceous_wetland) + s(b3km_pc_herbaceous_vegetation) + s(city_pc_cultivated) + s(city_pc_shrubs) + s(b500_pc_closed_forest_forest_other) + s(city_pc_urban) + s(region_pc_cultivated) + s(b1km_pc_permanent_water) + s(b5km_pc_bare) + s(region_pc_closed_forest_evergreen_needle) + s(elevation) + s(region_pc_closed_forest_forest_total) + s(region_pc_open_forest_evergreen_needle) + s(b5km_pc_closed_forest_evergreen_needle) + s(city_pc_closed_forest_evergreen_needle) + s(b500_pc_closed_forest_deciduous_broadleaf) + s(region_pc_permanent_water) + s(region_pc_open_forest_forest_other) + s(b500_pc_ocean) + s(city_pc_open_forest_forest_total) + s(city_pc_bare) + s(region_pc_bare) + s(city_pc_open_forest_forest_other) + s(city_pc_closed_forest_forest_total) + s(city_pc_closed_forest_forest_other) + s(region_pc_herbaceous_wetland) + s(region_pc_closed_forest_deciduous_broadleaf) + s(region_pc_urban) + s(city_pc_herbaceous_wetland) + s(pop_2015) + s(region_pc_closed_forest_forest_other) + s(city_pc_herbaceous_vegetation) + s(region_pc_closed_forest_evergreen_broadleaf) + s(region_pc_open_forest_deciduous_broadleaf) + s(city_pc_closed_forest_deciduous_broadleaf) + s(region_pc_closed_forest_forest_mixed) + s(b5km_pc_open_forest_evergreen_needle) + s(region_pc_open_forest_evergreen_broadleaf) + s(region_pc_ocean) + s(city_pc_open_forest_deciduous_broadleaf) + s(b5km_pc_closed_forest_forest_mixed) + s(region_pc_open_forest_forest_mixed) + s(city_pc_closed_forest_forest_mixed) + s(city_pc_ocean) + s(b5km_pc_closed_forest_evergreen_broadleaf) + s(region_pc_snow), data = dataset, method = "REML")
summary(model_gam)
```

```{r}
ggplot(data = dataset, aes(y = locality_project_richness, x= city_pc_cultivated)) +
 geom_point() +
 geom_smooth(method = "gam", formula = y ~ s(x))
```


```{r}
ggplot(data = dataset, aes(y = locality_project_richness, x= b500_pc_urban)) +
 geom_point() +
 geom_smooth(method = "gam", formula = y ~ s(x))
```


```{r}
m1 <- gam(locality_project_richness ~ s(b500_pc_urban), data = dataset, family = gaussian)
summary(m1)
plot(m1)
gam.check(m1)
```






